### 2014-11-05 cvpr15review.tex
first commint, including pdf etc. Later I will modify the .gitignore file

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% usepackages by Petr
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[table]{xcolor}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\definecolor{myRed}{HTML}{FF3333}
\definecolor{myGreen}{HTML}{33FF33}
\definecolor{maroon}{cmyk}{0,0.87,0.68,0.32}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Fisher vector places: learning compact image descriptors for place recognition}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The goal of this work is to localize a query photograph by finding other images depicting the same place in a large geotagged image database. The contributions of this work are three fold. First, we learn a {\em discriminative} yet {\em compact} descriptor of each image in the database. This is achieved by applying exemplar support vector machine (e-SVM) learning to compact Fisher vector descriptors extracted from database images. Second, we analyze the exemplar support vector machine objective and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data. Third, based on this analysis we demonstrate that the learnt and re-normalized descriptor could be directly used for matching, thus avoiding the need for expensive and tedious calibration typically needed for exemplar support vector machine methods. Place recognition results are shown on two image datasets of Google street-view images from Pittsburgh  and demonstrate the learnt representation consistently improves over the standard Fisher vector descriptors at different target dimensions. 
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

The goal of this work is to localize a query image by matching to a large database of geotagged street-level imagery.
This is an important problem with practical applications in robotics, augmented reality or navigation. This task is however very difficult. It is hard to distinguish different places, e.g. streets in a city, from each other. The imaged appearance of a place can change drastically due to factors such as  viewpoint, illumination or even changes over time.
%
Finally, with the emergence of planet-scale geotagged image collections, such as Google Street-view, the image databases are becoming very large.   
We estimate a single country like France is covered by more than 60 million street-level panoramas. Hence the fundamental challenge in place recognition lies now in designing robust, discriminative yet compact image representations.

In this work we build on the method of Gronat {\it et al.}~\cite{Gronat13} who represent each image in the database by a per-location classifier
that is trained to discriminate each place from other places in the database. At query time, the query image is classified by all per-location classifiers and assigned to a place with the highest classification score. The training of each classifier is performed using the per-exemplar support vector machine (e-SVM)~\cite{Malisiewicz11}, which takes the positive image as a single positive example and other far away images in the database as negative examples. 
The exemplar SVM is well suited for this task as street-level image collections typically contain only one or at most hand-full of images depicting the same place. The intuition is that the exemplar SVM can learn the important features that distinguish the particular place from other similar places  in the database.  While the results of~\cite{Gronat13} are promising they suffer from two important drawbacks. First, the learnt place specific representation is not compact, which prohibits its application to planet-scale street-level collections that are now becoming available~\cite{Klinger13}. Second, the per-exemplar classifiers require careful and time-consuming calibration.

In this work we address both these issues. 
First, we apply the exemplar SVM training to compact Fisher vector~\cite{Jegou2011,Perronnin2010} image descriptors, which results in a {\em discriminative} yet {\em compact} representation of each image in the database. Second, to avoid the expensive classifier calibration, we analyze the exemplar SVM cost and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data. As a result of this analysis, we demonstrate that after an appropriate normalization of the new re-weighted descriptor no further calibration is necessary. We show improved results on place recognition using learnt compact Fisher vector descriptors~\cite{Jegou2011} of different dimensionality.
%-------------------------------------------------------------------------
\section{Related work} 
\label{sec:related}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Large-scale visual place recognition} %\vspace{-3mm}
    The visual localization problem is typically treated as large-scale instance-level retrieval~\cite{Cummins09,Chen11,Gronat13,Knopp2010,Schindler07,Torii2013,Zamir10}, where images are represented using local invariant features~\cite{Lowe04} aggregated into the bag-of-visual-words~\cite{Csurka04,Sivic03} representation. The image database can be further augmented by 3D point clouds~\cite{Klinger13}, automatically reconstructed by large-scale structure from motion (SfM)~\cite{Agarwal-ICCV-2009,Klinger13}, which enables accurate prediction of query image camera position~\cite{Li12,Sattler12}. In this work we investigate learning a discriminative representation using the compact Fisher vector descriptors~\cite{Jegou12}. Fisher vector descriptors have shown excellent place recognition accuracy~\cite{Torii2013}. In this work we further improve their performance by discriminative learning.

\subsection*{Fisher vector image representations} %\vspace{-3mm}
    Fisher vector image representations have recently demonstrated excellent performance for a number of visual recognition tasks~\cite{Chatfield11,Jegou12,Krapac2011,Simonyan2013}. They are specially suited for retrieval applications since they are robust to image appearance variations and capture richer image statistics than the simple bag-of-visual-words (BOW) aggregation. However, the raw extracted Fisher vectors are typically high-dimensional, e.g.\ with 32,768 non-sparse dimensions, which is impractical for large-scale visual recognition and indexing applications. Hence, their dimensionality is often reduced by principal component analysis (PCA) and further quantized for efficient indexing using, e.g.\, a product quantizer~\cite{Jegou12}.  Other recent work has demonstrated improved performance in a face recognition application by finding discriminative projection using a large amount of training face data~\cite{Simonyan2013}. Our work is complementary to these methods as it operates on the projected low-dimensional descriptor and further learns discriminative re-weighting of the descriptor specific to each image in the database using per-exemplar support vector machine~\cite{Malisiewicz11}.

\subsection*{Per-exemplar support vector machine} %\vspace{-3mm}
    The exemplar support vector machine (e-SVM) has been used in a number of visual recognition tasks including category-level recognition~\cite{Malisiewicz11}, cross-domain retrieval~\cite{Shrivastava11}, scene parsing~\cite{Tighe13}, place recognition~\cite{Gronat13} or as an initialization  for more complex discriminative clustering models~\cite{Doersch12,Singh12}. The main idea is to train a linear support vector machine (SVM) classifier from a single positive example and a large number of negatives. The intuition is that the resulting weight vector will give a higher weight to the discriminative dimensions of the positive training data point and will down weight dimensions that are non-discriminative with respect to the negative training data. A key advantage is that each per-exemplar classifier can be trained independently and hence the learning can be heavily parallelized. The per-exemplar training brings however also an important drawback. As each classifier is trained independently a careful calibration of the resulting classifier scores is required~\cite{Gronat13,Malisiewicz11}.

\subsection*{Contributions} %\vspace{-3mm}
    The contributions of this work are threefold.
    First, we analyze the exemplar support vector machine objective and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data. Second, we demonstrate that after an appropriate normalization of the new re-weighted descriptor no further calibration is necessary. Third, we apply e-SVM training to compact Fisher vector descriptors for large-scale place recognition resulting in a {\em discriminative} yet {\em compact} representation of each image in the database. Place recognition results are shown on a dataset of 25k images of Pittsburgh and demonstrate the learnt representation consistently improves over the standard Fisher vector descriptors at different target dimensions.

\section{Learning compact place descriptors using per-exemplar SVM}
\label{sec:perExemplar}
   Each database image $j$ is represented by its L2-normalized Fisher vector $\Phi_j$. The goal is to learn a set of new L2-normalized Fisher vectors $\Psi_j$, one per each database image, such that at query time, given the Fisher vector $\Phi_q$ of an unknown query image, we retrieve the database image depicting the same location by finding the image $j^*$ with the highest score measured by a dot product
   %
   \begin{equation}
       j^*=\operatorname*{arg\;max}_{j} \Phi_q^T \Psi_j. 
       \label{eq:class}
   \end{equation}
   %  
   In other words, the aim is to replace each original database Fisher vector $\Phi_j$ with a new vector $\Psi_j$ that is more discriminative in the sense of separation from descriptors of images depicting other places. Inspired by~\cite{Gronat13}, we investigate applying the exemplar support vector machine (e-SVM)~\cite{Malisiewicz11} for this task. e-SVM learns a linear classifier $w_j^T\Phi+b_j$ given the descriptor $\Phi_j^+$ of place $j$ as a single positive example (with target label +1) and a large number of negative descriptors $\mathcal N_j$ from other places in the database (with target labels -1). The intuition of the exemplar SVM training~\cite{Malisiewicz11} is that the learnt weight vector $w_j$ will give a higher weight to the dimensions of the descriptor that are discriminative and will down-weight dimensions that are non-discriminative with respect to the negative training data collected from other far-away places.  The optimal $w_j$ and $b_j$ are obtained by minimizing the following objective  
      %
      \begin{equation}
         ||w_j||^{2} +C_1 \cdot h
            \left(
               w_j^T\Phi^+_j+b_j
            \right)
            +C_2\sum_{\Phi\in \mathcal N_j}h
            \left(
               -w_j^T\Phi-b_j
            \right),   
         \label{eq:obj} 
      \end{equation}
      %
   where $\Phi^+_j$ is the descriptor of the place $j$ as the positive data point, $\Phi$ are Fisher descriptors from negative training data $\mathcal N_j$ and $h$ is the hinge loss, $h(y) = \max(1-y,0)$. Note that the first term in~(\ref{eq:obj}) is the regularizer, the second term is the loss on the positive data weighted by scalar parameter $C_1$ and the third term is the loss on the negative data weighted by scalar parameter $C_2$. The objective is convex and can be minimized with respect to $w_j$ and $b_j$ using standard software packages such as~\cite{libsvm}. A key advantage is that the per-exemplar classifier for each place can be trained independently and hence the learning can be heavily parallelized. The downside of the independent training for each positive example is that the resulting scores have to be calibrated with respect to each other on additional data~\cite{Gronat13,Malisiewicz11}.

   \subsection*{Analysis of per-exemplar SVM objective} %\vspace{-0.2cm} 
      In this section, we analyze the exemplar SVM objective~(\ref{eq:obj}) and show the learnt and {\em re-normalized} weight vector $w_j$ can be interpreted as a new descriptor $\Psi_j$ that replaces the original positive training descriptor $\Phi^+_j$.  In particular, we show first that when the weight $C_2$ of the negative data in objective~(\ref{eq:obj}) goes to zero and the learnt $\Psi_j$ is identical to the original positive training data point $\Phi_j^+$.  Second, when $C_2>0$, the learnt $\Psi_j$ moves away from the positive $\Phi_j^+$ to increase its separation from the negative data.
      Details are given next.

      \paragraph{Case I: $C_2\rightarrow 0$.}
         The goal is to show that when the weight  $C_2$ of the negative data in objective~\eqref{eq:obj} goes towards zero the resulting hyperplane vector $w_j$ is parallel with the positive training descriptor $\Phi_j^+$. When $w_j$ is normalized to have unit L2 norm the two vectors are identical. First, let us decompose $w$ into parallel and orthogonal part with respect to the positive training data point $\Phi^+$ (in the following we omit index $j$ for brevity), i.e. $w=w^{\perp}+w^{||}$, where $(w^{\perp})^T \Phi^+ = 0$. Next, we observe that when the weight of the negative data diminishes ($C_2\rightarrow 0$), any non-zero component $w^{\perp}$ will increase the value of the objective. As a result, for $C_2\rightarrow 0$ the objective is minimized by $w^{||}$, i.e.\ the optimal $w$ is parallel with $\Phi^+$.

         In detail, for $w=w^{\perp}+w^{||}$ the objective~(\ref{eq:obj}) can be written as
            %
            \begin{align}
               \label{eq:decomposedOrig}
                 ||w^{\perp}+w^{||}||^{2} &+
                 C_1 \cdot h
                 \left(
                  (w^{\perp}+w^{||})^T\Phi^+ + b
                 \right) \\ \nonumber
                 &+
                 C_2\sum_{\Phi\in \mathcal N} h
                 \left(
                  -(w^{\perp}+w^{||})^T\Phi-b
                 \right).
            \end{align}
            %
         Note that the orthogonal part $w^{\perp}$ does not change the value of  the second term in~(\ref{eq:decomposedOrig}) because $(w^{\perp}+w^{||})^T\Phi^+=(w^{||})^T\Phi^+$, and hence~(\ref{eq:decomposedOrig}) reduces to
            %
            \begin{align} 
               \label{eq:decomposed} 
               ||w^{\perp}+w^{||}||^{2} &+
               C_1 \cdot h
               \left(
                   w^{||T}\Phi^+ +b_j
               \right) \\ \nonumber
               &+
               C_2\sum_{\Phi\in \mathcal N} h
               \left(
                   -(w^{\perp}+w^{||})^T\Phi-b
               \right).
            \end{align}
            %
         In the limit case as $C_2 \rightarrow 0$ any non-zero component $w^{\perp}$
         will increase the value of the objective~\eqref{eq:decomposed}. This can be seen by noting that the third term vanishes when $C_2 \rightarrow 0$ and hence the objective is dominated by the first two terms. Further, the second term in~\eqref{eq:decomposed} is independent of $w^{\perp}$. Finally, the first term will always increase for any non-zero value of $w^{\perp}$ as $||w^{\perp}+w^{||}||^{2} \geq ||w^{||}||$ for any $w^{\perp}\neq0$.

         As a result, in the limit case when $C_2 \rightarrow 0$ the optimal $w$ is parallel with $\Phi^+$. Note also, that when $C_2$ is exactly equal to zero, $C_2=0$, the optimal $w$ vanishes, i.e. the objective~\eqref{eq:decomposed} is minimized by trivial solution $||w||=0$ and $b_j=-1$. The effect of decreasing the parameter $C_2$ is illustrated in figure~\ref{fig:C2effect}.

      \paragraph{Case II: $C_2>0$.}
         When the weight $C_2$ of the negative data in the objective~\eqref{eq:decomposed} increases the direction of the optimal $w$ will be different from $w^{||}$ and will change to take into account the loss on the negative data points. Explicitly writing the hinge-loss $h(x) = \max(1-x,0)$ in the last term of~\eqref{eq:decomposed}, we see that $w$ will move in the direction that reduces $\sum_{\Phi\in \mathcal N}\max \left(1+w^T \Phi + b ,0 \right)$, i.e.\ that reduces the dot product $w^T \Phi$ on the negative examples that are active (support vectors).
            %
            \begin{figure}[t]
               \begin{center}
                  \subfigure[$C_2>0$ ]{
                     \centering
                     \includegraphics[width=0.45\linewidth]{imgs/figSVM01tight}
                  }
                  %        $C_2 \rightarrow 0$
                  \subfigure[$C_2 \rightarrow 0$]{
                     \centering
                     \includegraphics[width=0.45\linewidth]{imgs/figSVM02tight}
                  }
                  \caption{
                     {\bf An illustration of the effect of decreasing parameter $C_2$ in the exemplar support vector machine objective.} 
                     The positive exemplar $\Phi_j^+$ is shown in green. The negative data points are shown in red. All training data is L2 normalized to lie on a hyper-sphere. (a) For $C_2>0$, the normal $w_j$ of the optimal hyper-plane moves away from the direction given by the positive example $\Phi^+$ in a manner that reduces the loss on the negative data.  (b) As the parameter $C_2$ decreases the learnt $w_j$ becomes parallel to the positive training example $\Phi_j^+$ and its magnitude $||w_j||$ goes to 0.
                  }
                  \label{fig:C2effect}
               \end{center}
            \end{figure}

   \subsection*{Interpreting normalized $w$ as a new descriptor} %\vspace{-0.2cm} 
      The above analysis demonstrates that as $C_2$ decreases the normal of the optimal hyperplane $w$ that separates the positive exemplar $\Phi^+$ from negative data becomes parallel with $\Phi^+$, as shown in figure \ref{fig:C2effect}. As $C_2$ increases, the normal $w$ of the optimal hyper-plane moves away from the direction given by the positive example $\Phi^+$ in a manner that reduces the loss on the negative data. 
      This suggests that the learnt $w$ could be interpreted as a modified positive example $\Phi^+$, re-weighted to emphasize directions that separate $\Phi^+$ from the negative data. As discussed above $w$ is not normalized. As we wish to measure the similarity between descriptors by (the cosine of) their angle        
      given by equation \eqref{eq:class}, additional normalization of the learnt $w$ is necessary. Hence we define the new descriptor $\Psi_j$ as the normalized hyperplane normal $w_j$
         %
         \begin{equation}
            \label{eq:normalization}
            \Psi_j=\dfrac{w_j}{||w_j||}.
         \end{equation}

\section{Experimental evaluation}
\label{sec:exp}
   In this section we first describe the experimental set-up, then we give implementation details, and finally report results of the proposed approach on two datasets where we compare performance with raw Fisher vector matching and several baselines methods.

   \subsection{Experimental set-up}
      We perform experiments on a database of Google Street View images of Pittsburgh downloaded from the Internet. The data contains panoramas covering roughly an area of $1.3 \times 1.2 \; {\rm km}^2$.       
      Similar to~\cite{Chen11}, for each panorama we generate 12 overlapping perspective views corresponding to two different elevation angles to capture both the street-level scene and the building fa\c{c}ades, resulting in a total of 24 perspective views each with $90^\circ$ FOV and resolution of $960 \times 720$ pixels.
      For evaluation we have used two versions of this data. The first one was obtained from the authors of~\cite{Gronat13} ($25$k images). In the second version we download additional images to increase the dataset size to $55$k images. 
      As a query set with known ground truth GPS positions, we use the 8999 panoramas from the Google Street View research dataset. This dataset covers approximately the same area, but has been captured at a different time, and depicts the same places from different viewpoints and under different illumination conditions. For each test panorama, we generate a set of perspective images as described above. Finally, we randomly select out of all generated perspective views a subset of 4k images, which is used as a test set to evaluate the performance of the proposed approach.
      Since all the query images have associated GPS location we can compute their spatial distance from the database images returned by the matching method. We consider a query image to be correctly localized if the retrieved database image lies within a perimeter of $20m$ from the location of the query.
      %
      \begin{figure}[t!]
         \centering
         \includegraphics[width=\linewidth]{imgs/plotPitt25k}    
         \caption{
            \textbf{Evaluation on Pittsburgh 25k \cite{Gronat13} dataset.} The fraction of correctly recognized queries (recall@K, y-axis) vs. the number of top $K$ retrieved database images for different Fisher vector dimensions. The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions.
         }
         \label{fig:recall}
      \end{figure}

   \subsection{Implementation details}
      We first extract rootSIFT descriptors~\cite{Arandjelovic12} for each image. Following~\cite{Jegou12} we project the 128-dimensional SIFT descriptors to 64 dimensions using PCA. The projection matrix is learnt on a set of descriptors from 5,000 randomly selected database images. This has also the effect of decorrelating the SIFT descriptor. 
      The 64-dimensional SIFT descriptors are then aggregated into Fisher vectors using a Gaussian mixture model with $N=256$ components, which  results in a $2\times256\times64 = 32,768$-dimensional descriptor for each image. The Gaussian mixture model is learnt from descriptors extracted from 5,000 randomly sampled database images. 
      The  high-dimensional Fisher vector descriptors are then projected down to dimension $d\in\{128,512, 2048\}$ using PCA learnt from all available images in the database. 
      The resulting low dimensional Fisher vectors are then re-normalized to have unit L2-norm, which we found to be important in practice.

      \paragraph{Learning parameters and training data.}
         To learn the exemplar support vector machine for each database image $j$, the positive and negative training data are constructed as follows. The \emph{negative training set} $\mathcal N_j$ is obtained by: (i) finding the set of images with geographical distance greater than $200{\rm m}$; (ii)  sorting the images by decreasing value of similarity to image $j$ measured by the dot product between their respective Fisher vectors; (iii) taking the top $N=500$ ranked images as the negative set. In other words, the negative training data consists of the hard negative images, i.e. those that are similar to image $j$ but are far away from its geographical position, hence, cannot have the same visual content. The \emph{positive training set} $\mathcal P_j$
         consist of the original Fisher vector $\Phi_j$ of the image $j$.
         For the SVM training we use {\tt libsvm} \cite{libsvm}.
         We use the same $C_1$ and $C_2$ parameters for all per-exemplar classifiers, but find the optimal value of the parameters for each dimensionality of the Fisher vector by a grid search evaluating performance on a held out set.
         We observe that for different Fisher vector target dimensions the optimal value of parameter $C_1$ is quite stable (typically $C_1=1$) while the optimal parameter for $C_2$ varies between $10^{-6}$ to $10^{-1}$.
         To learn the new image representation for each database image $j$ we: (i) learn SVM from $\mathcal P_j$ and $N_j$ (see above); (ii) $L2$ normalize the learned $w_j$ using equation~\eqref{eq:normalization}; and (iii) use this re-normalized vector as the new image descriptor $\Psi_j$ for image $j$. At query time we compute the Fisher vector $\Phi_q$ of the query image and measure its similarity score to the learnt descriptors $\Psi_j$ for each database image by equation~\eqref{eq:class}.

   \subsection{Results}    
      For each database (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).

      We perform experiments on several target Fisher vector dimensions $d\in\{128,512,2048\}$. For each method we measure performance using the percentage of correctly recognized queries (Recall) similarly to, e.g.,~\cite{Chen11,Knopp2010,Sattler-BMVC12}. The query is correctly localized if at least one of the top $K$ retrieved database images is within $20$ meters from the ground truth position of the query. Results are shown for different values of $K$ in table~\ref{tab:recall}. For the Pittsburgh 25k we also show results in the form of a curve in figure~\ref{fig:recall}. The results clearly demonstrate the benefits of the learnt descriptors with respect to the standard Fisher vectors for all target dimensions and lengths of shortlist $K$. The benefits of discriminative learning are specially prominent for low-dimensional compact descriptors ($d=128$). 
      The proposed method also significantly outperforms the bag-of-visual-words baseline. Figure~\ref{fig:images} shows examples of place recognition results.

      \paragraph{Comparison to other methods.}
         On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the methods of~\cite{Gronat13} and~\cite{Knopp2010}, who report on the same testing data top $K=1$ recall of 36.5\% and 41.9\%, respectively (results taken from~\cite{Gronat13}). Our method outperforms~\cite{Knopp2010} already for dimension $d=128$ (37.8\%) and~\cite{Gronat13} for dimension $d=512$ (47.6\%). Furthermore, note that~\cite{Gronat13,Knopp2010} are based on a bag-of-visual-words representation, which typically needs to store between 1000-2000 non-zero visual words per image, which is significantly more than our learnt 128 or 512 dimensional descriptor.

      \paragraph{Memory complexity analysis.}
         Figure~\ref{fig:memory} compares the performance of the learnt discriminative descriptor (FV eSVM) to the raw Fisher vectors (FV) for different target dimensions. 
         The results demonstrate that for a given level of accuracy (y-axis) our method learns a more compact (lower-dimensional) representation (x-axis). For example, our learnt 128-dimensional descriptor achieves a similar accuracy (around 65\%) to the 256-dimensional raw Fisher descriptor essentially reducing the memory complexity to 50\% for the same level of performance.  Note that 
         similar to~\cite{Jegou12}, we observe decrease in performance at high-dimensions for both the baseline and our method.
         %
         \begin{figure}[t!]
            \centering
            \includegraphics[width=1.0\linewidth]{imgs/FVmemory}    
            \caption{
               \textbf{Memory complexity analysis.} 
               The fraction of correctly localized queries at the top 10 retrieved images (y-axis) for different Fisher vector dimensions (x-axis). The learnt descriptors by our method (FV e-SVM) clearly outperform the raw Fisher vector descriptors (FV) for all dimensions. Note that for a certain level of performance (y-axis) the proposed method learns a more memory efficient (lower dimensional, x-axis) descriptor.
            }
            \label{fig:memory}
         \end{figure}
         %
         %
         %
         \begin{table*}[t!]
            \begin{centering}
               \begin{tabularx}{0.75\linewidth}{|l|c c c c c|c c c c c|}
                  \hline 
                  \rowcolor{maroon!50}
                  Method: & \multicolumn{5}{c|}{25k Pittsburgh} & \multicolumn{5}{c|}{55k Pittsburgh} \\
                  \hline 
                  \hline 
                  \rowcolor{maroon!50}
                  recall@K [$\%$] & 1 & 2 & 5 & 10 & 20 & 1 & 2 & 5 & 10 & 20\\
                  \hline
                  \rowcolor{maroon!10}
                  BOW & 29.4 & 35.7 & 47.0 & 57.1 & 66.5 & 8.7 & 11.0 & 17.3 & 22.8 & 25.4  \\
                    \hline
                  \rowcolor{maroon!10}
                  FV128         & 33.6 & 41.8 & 52.0 & 59.8 & 67.7 & 10.9 & 14.1 & 20.2 & 26.4 & 33.2 \\
                  \rowcolor{maroon!10}
                  \textbf{FV128 e-SVM}   & \textbf{37.8}  & \textbf{46.1} & \textbf{56.9} & \textbf{64.9} & \textbf{72.6}  &
                                             \textbf{13.5}  &  \textbf{17.7}  &  \textbf{25.0}  &  \textbf{31.8}  &  \textbf{39.0} \\
                    \hline
                    \rowcolor{maroon!10}
                    FV512         & 44.3 & 51.7 & 61.4 & 68.7 & 75.2 & 17.3 &  21.1 &  28.4 &  34.2 &  40.3 \\
                    \rowcolor{maroon!10}
                    \textbf{FV512 e-SVM}   & \textbf{47.6}  & \textbf{55.4} & \textbf{65.1} & \textbf{72.4} & \textbf{78.8}  &
                                             \textbf{19.8} &  \textbf{25.1} &  \textbf{32.7}  & \textbf{38.7} &  \textbf{46.0} \\
                    \hline
                  \rowcolor{maroon!10}
                  FV2048        & 46.9  & 54.1 & 63.8 & 70.5 & 76.8 & 19.2 & 23.5 & 29.9 &  35.2 &  41.9 \\
                  \rowcolor{maroon!10}
                  \textbf{FV2048 e-SVM}  & \textbf{50.2} & \textbf{57.3} & \textbf{67.0} & \textbf{73.8} & \textbf{78.0} &
                    \textbf{20.8} & \textbf{25.9} & \textbf{33.1} & \textbf{38.7} & \textbf{45.9}\\
                  \hline
               \end{tabularx}
            \caption{ \textcolor{myRed}{}
                  The fraction of correctly recognized queries (recall@K) vs. the number of top $K\in\{1,2,5,10,20\}$ retrieved database images for different Fisher vector dimensions $d\in\{128,512,2048\}$. The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions on both the 25k and 55k Pittsburgh image datasets.     
            }
            \label{tab:recall}
            \end{centering}
         \end{table*}
         %
         %
         %
         \begin{figure*}[t!]
            %%%%%%%%%%% Example 1 %%%%%%%%%%%%%%%
            % QUERY image
            \begin{minipage}{0.34\linewidth}
               \centering
               \vspace{5mm}
               \includegraphics[height=40mm]{imgs/ex1/query.jpg}
            \end{minipage}
            % Retrieved images
            \begin{minipage}{0.75\linewidth}
               % FV e-SVM
               \begin{minipage}{\linewidth} 
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm1.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm2.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm3.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm4.jpg}}
               \end{minipage}
               \\
               \begin{minipage}{\linewidth}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV1.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV2.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV3.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV4.jpg}}
               \end{minipage} 
            \end{minipage}
            \\
            %%%%%%%%%%% Example 2 %%%%%%%%%%%%%%%
            \begin{minipage}{0.34\linewidth}
               \centering
               \vspace{0mm}
               \includegraphics[height=36mm]{imgs/ex2/query.jpg}
            \end{minipage}
            % Retrieved images
            \begin{minipage}{0.75\linewidth}
               % FV e-SVM
               \begin{minipage}{\linewidth} 
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm1.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm2.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm3.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm4.jpg}}
               \end{minipage}
               \\
               \begin{minipage}{\linewidth}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV1.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV2.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV3.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV4.jpg}}
               \end{minipage} 
            \end{minipage}
            \vspace{3mm}
            \\
            %%%%%%%%%%% Example 3 %%%%%%%%%%%%%%%
            \begin{minipage}{0.34\linewidth}
               \centering
               \vspace{0mm}
               \includegraphics[height=36mm]{imgs/ex3/query.jpg}
            \end{minipage}
            % Retrieved images
            \begin{minipage}{0.75\linewidth}
               % FV e-SVM
               \begin{minipage}{\linewidth} 
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm1.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FVsvm2.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm5.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm4.jpg}}
               \end{minipage}
               \\
               \begin{minipage}{\linewidth}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV1.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FV2.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV3.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV4.jpg}}
               \end{minipage} 
            \end{minipage}
            \vspace{3mm}
            \\
            %%%%%%%%%%% Example 4 %%%%%%%%%%%%%%%
            \begin{minipage}{0.34\linewidth}
               \centering
               \vspace{0mm}
               \includegraphics[height=36mm]{imgs/ex4/query.jpg}
            \end{minipage}
            % Retrieved images
            \begin{minipage}{0.75\linewidth}
               % FV e-SVM
               \begin{minipage}{\linewidth} 
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm1.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FVsvm2.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm5.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm4.jpg}}
               \end{minipage}
               \\
               \begin{minipage}{\linewidth}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV1.jpg}}
                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FV2.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV3.jpg}}
                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV4.jpg}}
               \end{minipage} 
            \end{minipage}
            %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
            \caption{
               Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by our learnt descriptors (top) and the raw Fisher vector descriptor baseline (bottom). For each method we show the top 4 matches from the database using 128-dimensional descriptors.        
            }
            \label{fig:images}
         \end{figure*}
         %
         %
         %
   \section{Conclusions}
      We have shown that a discriminative yet compact image representation for place recognition can be learnt using the exemplar support vector machine applied to Fisher vector image descriptors without the need for expensive and tedious calibration typical for other exemplar support vector machine methods. Our results show significant gains in place recognition performance compared to raw Fisher vector matching as well as other baselines. Our work opens-up the possibility of learning a compact and discriminative representation using other descriptors such as HOG~\cite{Dalal05} or the recently developed convolutional neural network features~\cite{Donahue13,Krizhevsky12,Oquab14,Sermanet13} as well as extending the analysis to other cost functions~\cite{Gharbi12,Hariharan12}.

\small{
   \bibliographystyle{ieee}
   \bibliography{shortstrings,vggroup,cvww_template,mybib}
}

\end{document}

### 2014-11-05 egpaper_for_review.tex
first commint, including pdf etc. Later I will modify the .gitignore file

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% usepackages by Petr
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[table]{xcolor}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for CVPR Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the CVPR 2015 web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
For CVPR 2015, the rules about paper length have changed, so please
read this section carefully. Papers, excluding the references section,
must be no longer than eight pages in length. The references section
will not be included in the page count, and there is no limit on the
length of the references section. For example, a paper of eight pages
with two pages of references would have a total length of 10 pages.
{\bf Unlike previous years, there will be no extra page charges for
  CVPR 2015.}

Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the CVPR 2015 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

Please direct any questions to the production editor in charge of these
proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
Fax (714) 761-1784.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2014-11-07 cvpr15review.tex
new figure, more examples in images, ubsections changed to paragraphs

@@
 
-\subsection*{Large-scale visual place recognition} %\vspace{-3mm}
+\paragraph{Large-scale visual place recognition} %\vspace{-3mm}
     The visual localization problem is typically treated as large-scale instance-level retrieval~\cite{Cummins09,Chen11,Gronat13,Knopp2010,Schindler07,Torii2013,Zamir10}, where images are represented using local invariant features~\cite{Lowe04} aggregated into the bag-of-visual-words~\cite{Csurka04,Sivic03} representation.
@@
 
-\subsection*{Fisher vector image representations} %\vspace{-3mm}
+\paragraph{Fisher vector image representations} %\vspace{-3mm}
     Fisher vector image representations have recently demonstrated excellent performance for a number of visual recognition tasks~\cite{Chatfield11,Jegou12,Krapac2011,Simonyan2013}.
@@
 
-\subsection*{Per-exemplar support vector machine} %\vspace{-3mm}
+\paragraph{Per-exemplar support vector machine} %\vspace{-3mm}
     The exemplar support vector machine (e-SVM) has been used in a number of visual recognition tasks including category-level recognition~\cite{Malisiewicz11}, cross-domain retrieval~\cite{Shrivastava11}, scene parsing~\cite{Tighe13}, place recognition~\cite{Gronat13} or as an initialization  for more complex discriminative clustering models~\cite{Doersch12,Singh12}.
@@
 
-\subsection*{Contributions} %\vspace{-3mm}
+\paragraph{Contributions} %\vspace{-3mm}
     The contributions of this work are threefold.
@@
 
-   \subsection*{Analysis of per-exemplar SVM objective} %\vspace{-0.2cm} 
+   \paragraph{Analysis of per-exemplar SVM objective} %\vspace{-0.2cm} 
       In this section, we analyze the exemplar SVM objective~(\ref{eq:obj}) and show the learnt and {\em re-normalized} weight vector $w_j$ can be interpreted as a new descriptor $\Psi_j$ that replaces the original positive training descriptor $\Phi^+_j$.
@@
 
-   \subsection*{Interpreting normalized $w$ as a new descriptor} %\vspace{-0.2cm} 
+   \paragraph{Interpreting normalized $w$ as a new descriptor} %\vspace{-0.2cm} 
       The above analysis demonstrates that as $C_2$ decreases the normal of the optimal hyperplane $w$ that separates the positive exemplar $\Phi^+$ from negative data becomes parallel with $\Phi^+$, as shown in figure \ref{fig:C2effect}.
@@
          %
+         \begin{figure*}
+            \include{myFigureWnorm}
+            \caption{
+                \textbf{Examples of correctly and incorrectly localized queries for the learnt Fisher vector representation.}
+                Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by the learnt Fisher vector representation \emph{w-norm} method (top) and the standard Fisher vector baseline (bottom) for dimension 128.
+Note that the proposed method is able to recognize the place depicted in the query image despite changes in viewpoint, illumination and partial occlusion by other objects (trees, lamps) and buildings.
+                Note that the baseline methods often finds images depicting the same buildings but in a distance whereas our learnt representation often finds a closer view better matching the content of the query.
+            }
+            \label{fig:images}
+         \end{figure*}
+         %
+         %
+         %
          \begin{table*}[t!]
@@
          %
-         \begin{figure*}[t!]
-            %%%%%%%%%%% Example 1 %%%%%%%%%%%%%%%
-            % QUERY image
-            \begin{minipage}{0.34\linewidth}
-               \centering
-               \vspace{5mm}
-               \includegraphics[height=40mm]{imgs/ex1/query.jpg}
-            \end{minipage}
-            % Retrieved images
-            \begin{minipage}{0.75\linewidth}
-               % FV e-SVM
-               \begin{minipage}{\linewidth} 
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm1.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm2.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm3.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm4.jpg}}
-               \end{minipage}
-               \\
-               \begin{minipage}{\linewidth}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV1.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV2.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV3.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV4.jpg}}
-               \end{minipage} 
-            \end{minipage}
-            \\
-            %%%%%%%%%%% Example 2 %%%%%%%%%%%%%%%
-            \begin{minipage}{0.34\linewidth}
-               \centering
-               \vspace{0mm}
-               \includegraphics[height=36mm]{imgs/ex2/query.jpg}
-            \end{minipage}
-            % Retrieved images
-            \begin{minipage}{0.75\linewidth}
-               % FV e-SVM
-               \begin{minipage}{\linewidth} 
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm1.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm2.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm3.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm4.jpg}}
-               \end{minipage}
-               \\
-               \begin{minipage}{\linewidth}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV1.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV2.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV3.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV4.jpg}}
-               \end{minipage} 
-            \end{minipage}
-            \vspace{3mm}
-            \\
-            %%%%%%%%%%% Example 3 %%%%%%%%%%%%%%%
-            \begin{minipage}{0.34\linewidth}
-               \centering
-               \vspace{0mm}
-               \includegraphics[height=36mm]{imgs/ex3/query.jpg}
-            \end{minipage}
-            % Retrieved images
-            \begin{minipage}{0.75\linewidth}
-               % FV e-SVM
-               \begin{minipage}{\linewidth} 
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm1.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FVsvm2.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm5.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm4.jpg}}
-               \end{minipage}
-               \\
-               \begin{minipage}{\linewidth}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV1.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FV2.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV3.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV4.jpg}}
-               \end{minipage} 
-            \end{minipage}
-            \vspace{3mm}
-            \\
-            %%%%%%%%%%% Example 4 %%%%%%%%%%%%%%%
-            \begin{minipage}{0.34\linewidth}
-               \centering
-               \vspace{0mm}
-               \includegraphics[height=36mm]{imgs/ex4/query.jpg}
-            \end{minipage}
-            % Retrieved images
-            \begin{minipage}{0.75\linewidth}
-               % FV e-SVM
-               \begin{minipage}{\linewidth} 
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm1.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FVsvm2.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm5.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm4.jpg}}
-               \end{minipage}
-               \\
-               \begin{minipage}{\linewidth}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV1.jpg}}
-                   \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FV2.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV3.jpg}}
-                   \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV4.jpg}}
-               \end{minipage} 
-            \end{minipage}
-            %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-            \caption{
-               Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by our learnt descriptors (top) and the raw Fisher vector descriptor baseline (bottom).
+         % \begin{figure*}[t!]
+         %    %%%%%%%%%%% Example 1 %%%%%%%%%%%%%%%
+         %    % QUERY image
+         %    \begin{minipage}{0.34\linewidth}
+         %       \centering
+         %       \vspace{5mm}
+         %       \includegraphics[height=40mm]{imgs/ex1/query.jpg}
+         %    \end{minipage}
+         %    % Retrieved images
+         %    \begin{minipage}{0.75\linewidth}
+         %       % FV e-SVM
+         %       \begin{minipage}{\linewidth} 
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm1.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm2.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm3.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm4.jpg}}
+         %       \end{minipage}
+         %       \\
+         %       \begin{minipage}{\linewidth}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV1.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV2.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV3.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV4.jpg}}
+         %       \end{minipage} 
+         %    \end{minipage}
+         %    \\
+         %    %%%%%%%%%%% Example 2 %%%%%%%%%%%%%%%
+         %    \begin{minipage}{0.34\linewidth}
+         %       \centering
+         %       \vspace{0mm}
+         %       \includegraphics[height=36mm]{imgs/ex2/query.jpg}
+         %    \end{minipage}
+         %    % Retrieved images
+         %    \begin{minipage}{0.75\linewidth}
+         %       % FV e-SVM
+         %       \begin{minipage}{\linewidth} 
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm1.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm2.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm3.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm4.jpg}}
+         %       \end{minipage}
+         %       \\
+         %       \begin{minipage}{\linewidth}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV1.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV2.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV3.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV4.jpg}}
+         %       \end{minipage} 
+         %    \end{minipage}
+         %    \vspace{3mm}
+         %    \\
+         %    %%%%%%%%%%% Example 3 %%%%%%%%%%%%%%%
+         %    \begin{minipage}{0.34\linewidth}
+         %       \centering
+         %       \vspace{0mm}
+         %       \includegraphics[height=36mm]{imgs/ex3/query.jpg}
+         %    \end{minipage}
+         %    % Retrieved images
+         %    \begin{minipage}{0.75\linewidth}
+         %       % FV e-SVM
+         %       \begin{minipage}{\linewidth} 
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm1.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FVsvm2.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm5.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm4.jpg}}
+         %       \end{minipage}
+         %       \\
+         %       \begin{minipage}{\linewidth}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV1.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FV2.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV3.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV4.jpg}}
+         %       \end{minipage} 
+         %    \end{minipage}
+         %    \vspace{3mm}
+         %    \\
+         %    %%%%%%%%%%% Example 4 %%%%%%%%%%%%%%%
+         %    \begin{minipage}{0.34\linewidth}
+         %       \centering
+         %       \vspace{0mm}
+         %       \includegraphics[height=36mm]{imgs/ex4/query.jpg}
+         %    \end{minipage}
+         %    % Retrieved images
+         %    \begin{minipage}{0.75\linewidth}
+         %       % FV e-SVM
+         %       \begin{minipage}{\linewidth} 
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm1.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FVsvm2.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm5.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm4.jpg}}
+         %       \end{minipage}
+         %       \\
+         %       \begin{minipage}{\linewidth}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV1.jpg}}
+         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FV2.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV3.jpg}}
+         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV4.jpg}}
+         %       \end{minipage} 
+         %    \end{minipage}
+         %    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+         %    \caption{
+         %       Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by our learnt descriptors (top) and the raw Fisher vector descriptor baseline (bottom).
 For each method we show the top 4 matches from the database using 128-dimensional descriptors.
-            }
-            \label{fig:images}
-         \end{figure*}
+         %    }
+         %    \label{fig:images}
+         % \end{figure*}
          %

### 2014-11-07 myFigureWnorm.tex
new figure, more examples in images, ubsections changed to paragraphs

        %%%%%%%%%%% Example 1 %%%%%%%%%%%%%%%
        \begin{minipage}{1.0\linewidth}
        \end{minipage}
        % QUERY image
        \begin{minipage}{0.34\linewidth}
            \centering
            \vspace{0mm}
            \includegraphics[trim = 45mm 40mm 45mm 30mm, clip=true,height=36mm]{imgs/Wnorm/exImproved02/query.jpg}
        \end{minipage}
        % Retrieved images
        \begin{minipage}{0.75\linewidth}
            % FV e-SVM
            \begin{minipage}{\linewidth} 
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved02/improvedPval01.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved02/improvedPval02.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved02/improvedPval03.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved02/improvedPval04.jpg}}
            \end{minipage}
            \\
            \begin{minipage}{\linewidth}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved02/improved01.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved02/improved02.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved02/improved03.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved02/improved04.jpg}}
            \end{minipage} 
        \end{minipage}
        \vspace{3mm}
        \\
        %%%%%%%%%%% Example 2 %%%%%%%%%%%%%%%
        \begin{minipage}{1.0\linewidth}
        \end{minipage}
        % QUERY image
        \begin{minipage}{0.34\linewidth}
            \centering
            \vspace{0mm}
            \includegraphics[trim = 45mm 40mm 45mm 30mm, clip=true,height=36mm]{imgs/Wnorm/exImproved05/query.jpg}
        \end{minipage}
        % Retrieved images
        \begin{minipage}{0.75\linewidth}
            % FV e-SVM
            \begin{minipage}{\linewidth} 
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved05/improvedPval01.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved05/improvedPval02.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved05/improvedPval03.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved05/improvedPval04.jpg}}
            \end{minipage}
            \\
            \begin{minipage}{\linewidth}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved05/improved01.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved05/improved02.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved05/improved03.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved05/improved04.jpg}}
            \end{minipage} 
        \end{minipage}
        \vspace{3mm}
        \\
        %%%%%%%%%%% Example 3 %%%%%%%%%%%%%%%
        \begin{minipage}{0.34\linewidth}
            \centering
            \vspace{0mm}
            \includegraphics[trim = 45mm 40mm 45mm 30mm, clip=true, height=36mm]{imgs/Wnorm/exImproved04/query.jpg}
        \end{minipage}
        % Retrieved images
        \begin{minipage}{0.75\linewidth}
            % FV e-SVM
            \begin{minipage}{\linewidth} 
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved04/improvedPval01.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved04/improvedPval02.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved04/improvedPval03.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved04/improvedPval04.jpg}}
            \end{minipage}
            \\
            \begin{minipage}{\linewidth}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved04/improved01.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved04/improved02.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved04/improved03.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exImproved04/improved04.jpg}}
            \end{minipage} 
        \end{minipage}
        \vspace{3mm}
        \\
        %%%%%%%%%%% MIX FAILURE CASES: good examples are Mix09 14 17 16 20
        %%%%%%%%%%% Example 4 %%%%%%%%%%%%%%%
        \begin{minipage}{0.34\linewidth}
            \centering
            \vspace{0mm}
            \includegraphics[trim = 45mm 40mm 45mm 30mm, clip=true, height=36mm]{imgs/Wnorm/exMix15/query.jpg}
        \end{minipage}
        % Retrieved images
        \begin{minipage}{0.75\linewidth}
            % FV e-SVM
            \begin{minipage}{\linewidth} 
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix15/mixPval01.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix15/mixPval02.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix15/mixPval03.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix15/mixPval04.jpg}}
            \end{minipage}
            \\
            \begin{minipage}{\linewidth}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix15/mix01.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix15/mix02.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix15/mix03.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix15/mix04.jpg}}
            \end{minipage} 
        \end{minipage}
        \vspace{3mm}
        \\
        %%%%%%%%%%% Example 5 %%%%%%%%%%%%%%%
        \begin{minipage}{0.34\linewidth}
            \centering
            \vspace{0mm}
            \includegraphics[trim = 45mm 40mm 45mm 30mm, clip=true, height=36mm]{imgs/Wnorm/exMix19/query.jpg}
        \end{minipage}
        % Retrieved images
        \begin{minipage}{0.75\linewidth}
            % FV e-SVM
            \begin{minipage}{\linewidth} 
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix19/mixPval01.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix19/mixPval02.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix19/mixPval03.jpg}}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix19/mixPval04.jpg}}
            \end{minipage}
            \\
            \begin{minipage}{\linewidth}
                \colorbox{myGreen}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix19/mix01.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix19/mix02.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix19/mix03.jpg}}
                \colorbox{myRed}{\includegraphics[trim = 35mm 30mm 35mm 30mm, clip=true, height=16mm]{imgs/Wnorm/exMix19/mix04.jpg}}
            \end{minipage} 
        \end{minipage}
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-11-10 cvpr15review.tex
minor changes

@@
 %%%%%%%%% TITLE
-\title{\LaTeX\ Fisher vector places: learning compact image descriptors for place recognition}
+\title{Fisher vector places: learning compact image descriptors for place recognition}
 
@@
 
-   \paragraph{Analysis of per-exemplar SVM objective} %\vspace{-0.2cm} 
+   \subsection{Analysis of per-exemplar SVM objective} %\vspace{-0.2cm} 
       In this section, we analyze the exemplar SVM objective~(\ref{eq:obj}) and show the learnt and {\em re-normalized} weight vector $w_j$ can be interpreted as a new descriptor $\Psi_j$ that replaces the original positive training descriptor $\Phi^+_j$.
@@
 
-   \paragraph{Interpreting normalized $w$ as a new descriptor} %\vspace{-0.2cm} 
+   \subsection{Interpreting normalized $w$ as a new descriptor} %\vspace{-0.2cm} 
       The above analysis demonstrates that as $C_2$ decreases the normal of the optimal hyperplane $w$ that separates the positive exemplar $\Phi^+$ from negative data becomes parallel with $\Phi^+$, as shown in figure \ref{fig:C2effect}.

### 2014-11-12 cvpr15review.tex
results updating, minor polish

@@
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{954} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 %%%%%%%%% TITLE
-\title{Fisher vector places: learning compact image descriptors for place recognition}
+\title{Fisher vector places: learning compact descriptors for place recognition}
 
@@
 This is achieved by applying exemplar support vector machine (e-SVM) learning to compact Fisher vector descriptors extracted from database images.
-Second, we analyze the exemplar support vector machine objective and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data.
-Third, based on this analysis we demonstrate that the learnt and re-normalized descriptor could be directly used for matching, thus avoiding the need for expensive and tedious calibration typically needed for exemplar support vector machine methods.
+Secondly, we analyze the exemplar support vector machine objective and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data.
+Finally, based on this analysis we demonstrate that the learnt and re-normalized descriptor could be directly used for matching, thus avoiding the need for expensive and tedious calibration typically needed for exemplar support vector machine methods.
 Place recognition results are shown on two image datasets of Google street-view images from Pittsburgh  and demonstrate the learnt representation consistently improves over the standard Fisher vector descriptors at different target dimensions.
@@
 This task is however very difficult.
-It is hard to distinguish different places, e.g.
-streets in a city, from each other.
+It is hard to distinguish different places, e.g.\ streets in a city, from each other.
 The imaged appearance of a place can change drastically due to factors such as  viewpoint, illumination or even changes over time.
@@
 We estimate a single country like France is covered by more than 60 million street-level panoramas.
-Hence the fundamental challenge in place recognition lies now in designing robust, discriminative yet compact image representations.
+Hence the fundamental challenge in place recognition lies now in designing robust, discriminative, yet compact, image representations.
 
-In this work we build on the method of Gronat {\it et al.}~\cite{Gronat13} who represent each image in the database by a per-location classifier
-that is trained to discriminate each place from other places in the database.
+In this work we build on the method of Gronat {\it et al.}~\cite{Gronat13} who represent each image in the database by a per-location classifier that is trained to discriminate each place from other places in the database.
 At query time, the query image is classified by all per-location classifiers and assigned to a place with the highest classification score.
 The training of each classifier is performed using the per-exemplar support vector machine (e-SVM)~\cite{Malisiewicz11}, which takes the positive image as a single positive example and other far away images in the database as negative examples.
-The exemplar SVM is well suited for this task as street-level image collections typically contain only one or at most hand-full of images depicting the same place.
+The exemplar SVM is well suited for this task as street-level image collections typically contain only one or at most a hand-full of images depicting the same place.
 The intuition is that the exemplar SVM can learn the important features that distinguish the particular place from other similar places  in the database.
@@
 \paragraph{Large-scale visual place recognition} %\vspace{-3mm}
-    The visual localization problem is typically treated as large-scale instance-level retrieval~\cite{Cummins09,Chen11,Gronat13,Knopp2010,Schindler07,Torii2013,Zamir10}, where images are represented using local invariant features~\cite{Lowe04} aggregated into the bag-of-visual-words~\cite{Csurka04,Sivic03} representation.
+    The visual localization problem is typically treated as a large-scale instance-level retrieval~\cite{Cummins09,Chen11,Gronat13,Knopp2010,Schindler07,Torii2013,Zamir10}, where images are represented using local invariant features~\cite{Lowe04} aggregated into the bag-of-visual-words~\cite{Csurka04,Sivic03} representation.
 The image database can be further augmented by 3D point clouds~\cite{Klinger13}, automatically reconstructed by large-scale structure from motion (SfM)~\cite{Agarwal-ICCV-2009,Klinger13}, which enables accurate prediction of query image camera position~\cite{Li12,Sattler12}.
@@
 However, the raw extracted Fisher vectors are typically high-dimensional, e.g.\ with 32,768 non-sparse dimensions, which is impractical for large-scale visual recognition and indexing applications.
-Hence, their dimensionality is often reduced by principal component analysis (PCA) and further quantized for efficient indexing using, e.g.\, a product quantizer~\cite{Jegou12}.
+Hence, their dimensionality is often reduced by principal component analysis (PCA) and further quantized for efficient indexing using, e.g.\ a product quantizer~\cite{Jegou12}.
 Other recent work has demonstrated improved performance in a face recognition application by finding discriminative projection using a large amount of training face data~\cite{Simonyan2013}.
@@
     First, we analyze the exemplar support vector machine objective and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data.
-Second, we demonstrate that after an appropriate normalization of the new re-weighted descriptor no further calibration is necessary.
-Third, we apply e-SVM training to compact Fisher vector descriptors for large-scale place recognition resulting in a {\em discriminative} yet {\em compact} representation of each image in the database.
+Secondly, we demonstrate that after an appropriate normalization of the new re-weighted descriptor no further calibration is necessary.
+Finally, we apply e-SVM training to compact Fisher vector descriptors for large-scale place recognition resulting in a {\em discriminative} yet {\em compact} representation of each image in the database.
 Place recognition results are shown on a dataset of 25k images of Pittsburgh and demonstrate the learnt representation consistently improves over the standard Fisher vector descriptors at different target dimensions.
@@
 \label{sec:perExemplar}
-   Each database image $j$ is represented by its L2-normalized Fisher vector $\Phi_j$.
-The goal is to learn a set of new L2-normalized Fisher vectors $\Psi_j$, one per each database image, such that at query time, given the Fisher vector $\Phi_q$ of an unknown query image, we retrieve the database image depicting the same location by finding the image $j^*$ with the highest score measured by a dot product
+   Each database image $j$ is represented by its L2-normalized Fisher vector $\Phi_j$. The goal is to learn a set of new L2-normalized Fisher vectors $\Psi_j$, one per each database image.
+   % such that at query time, 
+   \textcolor{maroon}{At query time,} given the Fisher vector $\Phi_q$ of an unknown query image, we retrieve the database image depicting the same location by finding the image $j^*$ with the highest score measured by a dot product
    %
@@
       %
-      \begin{equation}
-         ||w_j||^{2} +C_1 \cdot h
+      \begin{align}
+         \label{eq:obj}
+         ||w_j||^{2} &+C_1 \cdot h
             \left(
                w_j^T\Phi^+_j+b_j
-            \right)
-            +C_2\sum_{\Phi\in \mathcal N_j}h
+            \right)  \\ \nonumber
+            &+C_2\sum_{\Phi\in \mathcal N_j}h
             \left(
@@
             \right),    
-         \label{eq:obj} 
-      \end{equation}
+      \end{align}
       %
@@
       \paragraph{Case I: $C_2\rightarrow 0$.}
-         The goal is to show that when the weight  $C_2$ of the negative data in objective~\eqref{eq:obj} goes towards zero the resulting hyperplane vector $w_j$ is parallel with the positive training descriptor $\Phi_j^+$.
+         The goal is to show that when the weight  $C_2$ of the negative data in objective~\eqref{eq:obj} goes towards zero, the resulting hyperplane vector $w_j$ is parallel with the vector of positive training descriptor $\Phi_j^+$.
 When $w_j$ is normalized to have unit L2 norm the two vectors are identical.
@@
                   BOW         & 29.4 & 35.7 & 47.0 & 57.1 & 66.5 & 8.7 & 11.0 & 17.3 & 22.8 & 25.4  \\
+                  BOW raw SVM & 6.4  &  8.1 & 13.5 & 17.5 & 20.5 & & & & & \\ 
+                  BOW e-SVM   & 32.2 & 37.3 & 46.2 & 54.4 & 63.3 & & & & & \\
                     \hline
@@
                   FV128         & 33.6 & 41.8 & 52.0 & 59.8 & 67.7 & 10.9 & 14.1 & 20.2 & 26.4 & 33.2 \\
+                  FV128 raw SVM & 32.4 & 41.1 & 52.6 & 60.4 & 68.4 & & & & & \\
                   \rowcolor{maroon!10}

### 2014-11-13 rebuttal.tex
rebuttal init

We thank reviewers for their time and valuable comments. We will
update the paper as outlined below.

Why L2 normalization works (R18,R34,R38)
The proposed re-normalization procedure can be interpreted as a simple
form of affine calibration where the uncalibrated SVM score s(x) = w^T
x + b is transformed into a calibrated score f(x) = alpha * s(x) +
beta, where alpha = 1/||w|| and beta = -b*alpha. Note that the bias
term b is not ignored but used to compute f(x). The intuition is that
for L2 normalized descriptors x computing the calibrated score f(x)
corresponds to computing the normalized cross-correlation between
vectors w and x. This was found to work well in retrieval (see e.g.
Sivic and Zisserman, ICCV 2003 [32]) or matching whitened HOG
descriptors [11,13] (see e.g. [Doersch et al., Mid-Level Visual
Element Discovery as discriminative Mode Seeking, NIPS 2013]), but has
not yet been used in conjunction with SVMs as done in this work. Note
also that the affine calibration can be computed offline and does not
need any additional computation or storage at query time compared to
the p-value calibration of Gronat et al. [12].

-> Section 3.2

Comparison with p-value calibration of Gronat et al. [12] (R18,R34,R38)
We have compared the proposed method with the p-value calibration of
(Gronat et al.[12]) applied to Fisher vectors. The results show that
our method significantly outperforms the p-value calibration (37.8%
recall@1 vs. 32.3% recall@1; 56.9% recall@5 vs. 50.0% recall@5) for
the Fisher vector of dimension 128. Similar gains are observed for
other FV dimensions.

-> Now in tables. Please discuss in "Comparison to other methods"

Applying the proposed method to other descriptors (R18, R38)
The proposed approach can be applied to other descriptors beyond
Fisher vectors. To demonstrate this we have applied the proposed
calibration by re-normalization to the bag-of-visual-words descriptor
used in (Gronat et al.[12]) and observed improvement from 29.4%
recall@K=1 (vanilla bag-of-visual-words) to 32.6% recall@K=1 (e-SVM
with the proposed calibration by renormalization). For
bag-of-visual-words, the e-SVM with p-value calibration gives
comparable results (33.6% recall@K=1) but at an increased training
cost and a significantly higher required memory footprint at query
time, which makes the method very hard to scale-up to database sizes
beyond 200k images.

-> Create new paragraph in the result section "Applying the proposed
method to other descriptors".
Refer to table.

Significance
- The exemplar SVM has been recently used for a number of recognition
task. This paper describes a simple procedure to avoid calibration of
the exemplar SVM score at query time by re-normalizing the learnt SVM
weights.

- We demonstrate that proposed method is applicable to two different
descriptors, the bag-of-visual-words and Fisher vectors.
-> Conclusion

- We show the method performs on par or better than other competing
calibration methods for the task of large-scale place recognition.

- We believe the paper is significant and could be adopted by others
because the method is simple, scalable, does not require additional
storage or computation at query time and could be applied for other
tasks that use exemplar SVM beyond the addressed place recognition
application.

Rejecting query images that are out of the database (R18)
We agree with R18 that the method cannot reject query images that are
out of the database. Similar to other retrieval methods, we address a
ranking problem and not a classification one. Given a query image the
goal is to create a ranked list of N best candidate images. These
candidates can be further verified by another more expensive method
(e.g. geometric verification [Philbin et al., Object retrieval with
large vocabularies and fast spatial matching, CVPR 2007, Knopp et al.,
Avoiding confusing features in place recognition, ECCV 2010 ]) to
reject false positives or to reject a query that comes from an unseen
place.

Other comments:
- Correction to figure 4 (R34)
Reviewer R34 is right, both the second (1st row) and the third (2nd
row) retrieved images for the second query example should be marked as
wrong. We will correct the figure for the next revision.
done

- Clarification of comparison to other works, L313-315 (R34)
We compare our method to the results from [12] who re-implemented [17]
and reported the results on the Pittsburgh 25k dataset.
results are in tables.

- Notation (R34)
We will improve the notation by showing vectors as bolds following the
suggestion from R34.
-> todo?

- Lower performance for high dimensional FV (R34)
It is known that dimensionality reduction can have a positive effect
on the FV performance, where lower dimensional descriptors can
outperform higher dimensional descriptors. This is a known effect also
observed in previous work, see e.g. Table 1 in [15].
- add comment to result section with a citaiton.

- Details of the bag-of-visual-words experiment (R38)
We use the same setup as [12] except that our descriptors are
rootSIFTs instead of SURFs used in [12].

-> Make sure we mention what do.

### 2014-11-13 cvpr15review.tex
rebuttal init

@@
 \definecolor{maroon}{cmyk}{0,0.87,0.68,0.32}
+\definecolor{petr}{HTML}{3333FF}
 
@@
 
-\paragraph{Large-scale visual place recognition} %\vspace{-3mm}
+\paragraph{Large-scale visual place recognition.} %\vspace{-3mm}
     The visual localization problem is typically treated as a large-scale instance-level retrieval~\cite{Cummins09,Chen11,Gronat13,Knopp2010,Schindler07,Torii2013,Zamir10}, where images are represented using local invariant features~\cite{Lowe04} aggregated into the bag-of-visual-words~\cite{Csurka04,Sivic03} representation.
@@
 
-\paragraph{Fisher vector image representations} %\vspace{-3mm}
+\paragraph{Fisher vector image representations.} %\vspace{-3mm}
     Fisher vector image representations have recently demonstrated excellent performance for a number of visual recognition tasks~\cite{Chatfield11,Jegou12,Krapac2011,Simonyan2013}.
@@
 
-\paragraph{Per-exemplar support vector machine} %\vspace{-3mm}
+\paragraph{Per-exemplar support vector machine.} %\vspace{-3mm}
     The exemplar support vector machine (e-SVM) has been used in a number of visual recognition tasks including category-level recognition~\cite{Malisiewicz11}, cross-domain retrieval~\cite{Shrivastava11}, scene parsing~\cite{Tighe13}, place recognition~\cite{Gronat13} or as an initialization  for more complex discriminative clustering models~\cite{Doersch12,Singh12}.
@@
 
-\paragraph{Contributions} %\vspace{-3mm}
+\paragraph{Contributions.} %\vspace{-3mm}
     The contributions of this work are threefold.
@@
    % such that at query time, 
-   \textcolor{maroon}{At query time,} given the Fisher vector $\Phi_q$ of an unknown query image, we retrieve the database image depicting the same location by finding the image $j^*$ with the highest score measured by a dot product
+   \textcolor{petr}{At query time,} given the Fisher vector $\Phi_q$ of an unknown query image, we retrieve the database image depicting the same location by finding the image $j^*$ with the highest score measured by a dot product
    %
@@
 
+      \textcolor{petr}{
+        The proposed re-normalization procedure can be interpreted as a simple form of affine calibration where the uncalibrated SVM score $s(x)=w^T x+b$ is transformed into a calibrated score $f(x)=\alpha s(x)+\beta$, where $\alpha = 1/||w||$ and $\beta = -b\alpha$.
+Note that the bias term b is not ignored but used to compute $f(x)$.
+The intuition is that for L2 normalized descriptors x computing the calibrated score $f(x)$ corresponds to computing the normalized cross-correlation between vectors w and x.
+This was found to work well in retrieval (see e.g.
+Sivic and Zisserman, ICCV 2003 [32]) or matching whitened HOG descriptors [11,13] (see e.g.
+[Doersch et al., Mid-Level Visual Element Discovery as discriminative Mode Seeking, NIPS 2013]), but has not yet been used in conjunction with SVMs as done in this work.
+Note also that the affine calibration can be computed offline and does not need any additional computation or storage at query time compared to the p-value calibration of Gronat et al.
+[12].
+      }
+
 \section{Experimental evaluation}
@@
 
+      \paragraph{Applying the proposed method to other descriptors}
+        \textcolor{petr}{TODO:  
+          Applying the proposed method to other descriptors (R18, R38) The proposed approach can be applied to other descriptors beyond Fisher vectors.
+To demonstrate this we have applied the proposed calibration by re-normalization to the bag-of-visual-words descriptor used in (Gronat et al.[12]) and observed improvement from 29.4\% recall@K=1 (vanilla bag-of-visual-words) to 32.6\% recall@K=1 (e-SVM with the proposed calibration by renormalization).
+For bag-of-visual-words, the e-SVM with p-value calibration gives comparable results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method very hard to scale-up to database sizes beyond 200k images.
+        }
+
       \paragraph{Comparison to other methods.}
@@
 
+        \textcolor{petr}{ TODO:
+          We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors.
+The results show that our method significantly outperforms the p-value calibration (37.8\% recall@1 vs.
+32.3\% recall@1; 56.9\% recall@5 vs.
+50.0\% recall@5) for the Fisher vector of dimension 128.
+Similar gains are observed for other FV dimensions.
+        }
       \paragraph{Memory complexity analysis.}
@@
       We have shown that a discriminative yet compact image representation for place recognition can be learnt using the exemplar support vector machine applied to Fisher vector image descriptors without the need for expensive and tedious calibration typical for other exemplar  support vector machine methods.
+      \textcolor{petr}{We demonstrate that proposed method is applicable to two different descriptors, the bag-of-visual-words and Fisher vectors.}
       Our results show significant gains in place recognition performance compared to raw Fisher vector matching as well as other baselines.

### 2014-11-13 cvpr15review.tex
text edit: results, conclusions, table spit: captions, plot: fixed BOW to SURF

@@
 \usepackage[table]{xcolor}
+\usepackage{hyphenat}
 
@@
 As discussed above $w$ is not normalized.
-As we wish to measure the similarity between descriptors by (the cosine of) their angle
-      given by equation \eqref{eq:class}, additional normalization of the learnt $w$ is necessary. Hence we define the new descriptor $\Psi_j$ as the normalized hyperplane normal $w_j$
+As we wish to measure the similarity between descriptors by (the cosine of) their angle given by equation \eqref{eq:class}, additional normalization of the learnt $w$ is necessary.
+Hence we define the new descriptor $\Psi_j$ as the normalized hyperplane normal $w_j$
          %
@@
 
-      \textcolor{petr}{
-        The proposed re-normalization procedure can be interpreted as a simple form of affine calibration where the uncalibrated SVM score $s(x)=w^T x+b$ is transformed into a calibrated score $f(x)=\alpha s(x)+\beta$, where $\alpha = 1/||w||$ and $\beta = -b\alpha$.
+      \textcolor{petr}{%TODO: \emph{we should't speak about calibration, we shoud address not ignoring $b$}\\
+         Notice that even the new descriptor $\Phi_j$ is obtained by normalization of the learnt hyperplane $w_j$, the bias $b$ form equation~\eqref{eq:decomposed} is not ignored.
+Indeed, the bias term in convex objective~\eqref{eq:obj} is affecting the learnt the hyperplane.
+         %\\
+         %The proposed re-normalization procedure can be interpreted as a simple form of affine calibration where the uncalibrated SVM score $s(x)=w^T x+b$ is transformed into a calibrated score $f(x)=\alpha s(x)+\beta$, where $\alpha = 1/||w||$ and $\beta = -b\alpha$.
 Note that the bias term b is not ignored but used to compute $f(x)$.
@@
          \centering
-         \includegraphics[width=\linewidth]{imgs/plotPitt25k}    
+         \includegraphics[width=\linewidth]{imgs/plotPitt25kSURF}    
          \caption{
@@
    \subsection{Results}  
+      \textcolor{petr}{TODO: comment results from the table - raw SVM BOW/FV}  
       For each database (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).
@@
 
-      \paragraph{Applying the proposed method to other descriptors}
-        \textcolor{petr}{TODO:  
-          Applying the proposed method to other descriptors (R18, R38) The proposed approach can be applied to other descriptors beyond Fisher vectors.
-To demonstrate this we have applied the proposed calibration by re-normalization to the bag-of-visual-words descriptor used in (Gronat et al.[12]) and observed improvement from 29.4\% recall@K=1 (vanilla bag-of-visual-words) to 32.6\% recall@K=1 (e-SVM with the proposed calibration by renormalization).
+      \paragraph{Applying the method to other descriptors.}
+        \textcolor{petr}{ 
+          The proposed approach can be applied to other descriptors beyond Fisher vectors.
+To demonstrate this we have applied the proposed method to the bag-of-visual-words descriptor and observed improvement from 28.7\% recall@K=1 (vanilla bag-of-visual-words) to 31.8\% recall@K=1 (e-SVM).
 For bag-of-visual-words, the e-SVM with p-value calibration gives comparable results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method very hard to scale-up to database sizes beyond 200k images.
@@
 
-        \textcolor{petr}{ TODO:
-          We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors.
+        \textcolor{petr}{
+         We also performed p-val calibration proposed by Gronat et al.~\cite{Gronat13} on e-SVM Fisher vectors.
+We found that the calibration did not perform for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128).
+When examining the results, we believe this may be attributed to the fact that Fisher vectors are low dimensional compared to the extremely high-dimensional (d=100,000) bag-of-visual-words representation, which affects the distribution of the classifier scores on the negative test data.
+          %We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors.
 The results show that our method significantly outperforms the p-value calibration (37.8\% recall@1 vs.
-32.3\% recall@1; 56.9\% recall@5 vs.
+32.3\% recall@1; 56.9\%recall@5 vs.
 50.0\% recall@5) for the Fisher vector of dimension 128.
@@
          \end{figure}
+         \begin{table}[htb]
+            \begin{centering}
+               \include{table25k}
+            \caption{ \textbf{Results on Pittsburgh 25k dataset.}
+                  The fraction of correctly recognized queries (recall@K)
+                  \textcolor{petr}{
+                     in top $K\in\{1,2,5,10,20\}$ retrieved images.
+                     Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions.The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
+                  } 
+                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions on both the 25k and 55k Pittsburgh image datasets.
+            }
+            \label{tab:recall}
+            \end{centering}
+         \end{table}
+
+         \begin{table}[htb]
+            \begin{centering}
+               \include{table55k}
+               \caption{ \textbf{Results on Pittsburgh 55k dataset.}
+                  The fraction of correctly recognized queries (recall@K)
+                  \textcolor{petr}{
+                  in top $K\in\{1,2,5,10,20\}$ retrieved images.
+                  The proposed method (\emph{e-SVM}) has been applied to Fisher vectors compressed to different dimensions.
+                  } 
+                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions on both the 25k and 55k Pittsburgh image datasets.
+               }
+            \label{tab:recall2}
+            \end{centering}
+         \end{table}
          %
@@
          %
-         \begin{figure*}
+         \begin{figure*}[h]
             \include{myFigureWnorm}
@@
          %
-         \begin{table*}[t!]
-            \begin{centering}
-               \begin{tabularx}{0.75\linewidth}{|l|c c c c c|c c c c c|}
-                  \hline 
-                  \rowcolor{maroon!50}
-                  Method: & \multicolumn{5}{c|}{25k Pittsburgh} & \multicolumn{5}{c|}{55k Pittsburgh} \\
-                  \hline 
-                  \hline 
-                  \rowcolor{maroon!50}
-                  recall@K [$\%$] & 1 & 2 & 5 & 10 & 20 & 1 & 2 & 5 & 10 & 20\\
-                  \hline
-                  \rowcolor{maroon!10}
-                  BOW         & 29.4 & 35.7 & 47.0 & 57.1 & 66.5 & 8.7 & 11.0 & 17.3 & 22.8 & 25.4  \\
-                  BOW raw SVM & 6.4  &  8.1 & 13.5 & 17.5 & 20.5 & & & & & \\ 
-                  BOW e-SVM   & 32.2 & 37.3 & 46.2 & 54.4 & 63.3 & & & & & \\
-                    \hline
-                  \rowcolor{maroon!10}
-                  FV128         & 33.6 & 41.8 & 52.0 & 59.8 & 67.7 & 10.9 & 14.1 & 20.2 & 26.4 & 33.2 \\
-                  FV128 raw SVM & 32.4 & 41.1 & 52.6 & 60.4 & 68.4 & & & & & \\
-                  \rowcolor{maroon!10}
-                  \textbf{FV128 e-SVM}   & \textbf{37.8}  & \textbf{46.1} & \textbf{56.9} & \textbf{64.9} & \textbf{72.6}  &
-                                             \textbf{13.5}  &  \textbf{17.7}  &  \textbf{25.0}  &  \textbf{31.8}  &  \textbf{39.0} \\
-                    \hline
-                    \rowcolor{maroon!10}
-                    FV512         & 44.3 & 51.7 & 61.4 & 68.7 & 75.2 & 17.3 &  21.1 &  28.4 &  34.2 &  40.3 \\
-                    \rowcolor{maroon!10}
-                    \textbf{FV512 e-SVM}   & \textbf{47.6}  & \textbf{55.4} & \textbf{65.1} & \textbf{72.4} & \textbf{78.8}  &
-                                             \textbf{19.8} &  \textbf{25.1} &  \textbf{32.7}  & \textbf{38.7} &  \textbf{46.0} \\
-                    \hline
-                  \rowcolor{maroon!10}
-                  FV2048        & 46.9  & 54.1 & 63.8 & 70.5 & 76.8 & 19.2 & 23.5 & 29.9 &  35.2 &  41.9 \\
-                  \rowcolor{maroon!10}
-                  \textbf{FV2048 e-SVM}  & \textbf{50.2} & \textbf{57.3} & \textbf{67.0} & \textbf{73.8} & \textbf{78.0} &
-                    \textbf{20.8} & \textbf{25.9} & \textbf{33.1} & \textbf{38.7} & \textbf{45.9}\\
-                  \hline
-               \end{tabularx}
-            \caption{ \textcolor{myRed}{}
-                  The fraction of correctly recognized queries (recall@K) vs.
-the number of top $K\in\{1,2,5,10,20\}$ retrieved database images for different Fisher vector dimensions $d\in\{128,512,2048\}$.
-The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions on both the 25k and 55k Pittsburgh image datasets.
-            }
-            \label{tab:recall}
-            \end{centering}
-         \end{table*}
-         %
-         %
-         %
-         % \begin{figure*}[t!]
-         %    %%%%%%%%%%% Example 1 %%%%%%%%%%%%%%%
-         %    % QUERY image
-         %    \begin{minipage}{0.34\linewidth}
-         %       \centering
-         %       \vspace{5mm}
-         %       \includegraphics[height=40mm]{imgs/ex1/query.jpg}
-         %    \end{minipage}
-         %    % Retrieved images
-         %    \begin{minipage}{0.75\linewidth}
-         %       % FV e-SVM
-         %       \begin{minipage}{\linewidth} 
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm1.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm2.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm3.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex1/FVsvm4.jpg}}
-         %       \end{minipage}
-         %       \\
-         %       \begin{minipage}{\linewidth}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV1.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV2.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV3.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex1/FV4.jpg}}
-         %       \end{minipage} 
-         %    \end{minipage}
-         %    \\
-         %    %%%%%%%%%%% Example 2 %%%%%%%%%%%%%%%
-         %    \begin{minipage}{0.34\linewidth}
-         %       \centering
-         %       \vspace{0mm}
-         %       \includegraphics[height=36mm]{imgs/ex2/query.jpg}
-         %    \end{minipage}
-         %    % Retrieved images
-         %    \begin{minipage}{0.75\linewidth}
-         %       % FV e-SVM
-         %       \begin{minipage}{\linewidth} 
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm1.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm2.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm3.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex2/FVsvm4.jpg}}
-         %       \end{minipage}
-         %       \\
-         %       \begin{minipage}{\linewidth}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV1.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV2.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV3.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex2/FV4.jpg}}
-         %       \end{minipage} 
-         %    \end{minipage}
-         %    \vspace{3mm}
-         %    \\
-         %    %%%%%%%%%%% Example 3 %%%%%%%%%%%%%%%
-         %    \begin{minipage}{0.34\linewidth}
-         %       \centering
-         %       \vspace{0mm}
-         %       \includegraphics[height=36mm]{imgs/ex3/query.jpg}
-         %    \end{minipage}
-         %    % Retrieved images
-         %    \begin{minipage}{0.75\linewidth}
-         %       % FV e-SVM
-         %       \begin{minipage}{\linewidth} 
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm1.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FVsvm2.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm5.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FVsvm4.jpg}}
-         %       \end{minipage}
-         %       \\
-         %       \begin{minipage}{\linewidth}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV1.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex3/FV2.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV3.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex3/FV4.jpg}}
-         %       \end{minipage} 
-         %    \end{minipage}
-         %    \vspace{3mm}
-         %    \\
-         %    %%%%%%%%%%% Example 4 %%%%%%%%%%%%%%%
-         %    \begin{minipage}{0.34\linewidth}
-         %       \centering
-         %       \vspace{0mm}
-         %       \includegraphics[height=36mm]{imgs/ex4/query.jpg}
-         %    \end{minipage}
-         %    % Retrieved images
-         %    \begin{minipage}{0.75\linewidth}
-         %       % FV e-SVM
-         %       \begin{minipage}{\linewidth} 
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm1.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FVsvm2.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm5.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FVsvm4.jpg}}
-         %       \end{minipage}
-         %       \\
-         %       \begin{minipage}{\linewidth}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV1.jpg}}
-         %           \colorbox{myGreen}{\includegraphics[height=16mm]{imgs/ex4/FV2.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV3.jpg}}
-         %           \colorbox{myRed}{\includegraphics[height=16mm]{imgs/ex4/FV4.jpg}}
-         %       \end{minipage} 
-         %    \end{minipage}
-         %    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-         %    \caption{
-         %       Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by our learnt descriptors (top) and the raw Fisher vector descriptor baseline (bottom).
-For each method we show the top 4 matches from the database using 128-dimensional descriptors.
-         %    }
-         %    \label{fig:images}
-         % \end{figure*}
-         %
-         %
-         %
+
    \section{Conclusions}

### 2014-11-13 cvpr15review.tex
polish + gitignore

@@
       \textcolor{petr}{%TODO: \emph{we should't speak about calibration, we shoud address not ignoring $b$}\\
-         Notice that even the new descriptor $\Phi_j$ is obtained by normalization of the learnt hyperplane $w_j$, the bias $b$ form equation~\eqref{eq:decomposed} is not ignored.
+         The intuition is that for L2 normalized query descriptors $\Phi_q$ computing the calibrated score $f(x)$ corresponds to computing the normalized cross-correlation between vectors $\Psi_j$ and $\Phi_q$.
+This was found to work well in retrieval (see e.g.~\cite{Sivic03}) or matching whitened HOG descriptors \cite{Gharbi12, Hariharan12}, but has not yet been used in conjunction with SVMs.
+         \\
+         Notice that even the new descriptor $\Psi_j$ is obtained by normalization of the learnt hyperplane $w_j$, the bias $b$ form equation~\eqref{eq:decomposed} is not ignored.
 Indeed, the bias term in convex objective~\eqref{eq:obj} is affecting the learnt the hyperplane.
@@
    \subsection{Results}  
-      \textcolor{petr}{TODO: comment results from the table - raw SVM BOW/FV}  
       For each database (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).
@@
 The query is correctly localized if at least one of the top $K$ retrieved database images is within $20$ meters from the ground truth position of the query.
-Results are shown for different values of $K$ in table~\ref{tab:recall}.
+Results are shown for different values of $K$ in tables~\ref{tab:recall} and \ref{tab:recall2}.
 For the Pittsburgh 25k we also show results in the form of a curve in figure~\ref{fig:recall}.
@@
 
-      \paragraph{Applying the method to other descriptors.}
+      \paragraph{Applying our learning method to other descriptors.}
         \textcolor{petr}{ 
@@
 For bag-of-visual-words, the e-SVM with p-value calibration gives comparable results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method very hard to scale-up to database sizes beyond 200k images.
+The results are given in table \ref{tab:recall}.
         }
@@
       \paragraph{Comparison to other methods.}
-         On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the methods of~\cite{Gronat13} and~\cite{Knopp2010}, who report on the same testing data top $K=1$ recall of 36.5\% and 41.9\%, respectively (results taken from~\cite{Gronat13}).
+         %On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the methods of~\cite{Gronat13} and~\cite{Knopp2010}, who report on the same testing data top $K=1$ recall of 36.5\% and 41.9\%, respectively (results taken from~\cite{Gronat13}).
 Our method outperforms~\cite{Knopp2010} already for dimension $d=128$ (37.8\%) and~\cite{Gronat13} for dimension $d=512$ (47.6\%).
 Furthermore, note that~\cite{Gronat13,Knopp2010} are based on a bag-of-visual-words representation, which typically needs to store between 1000-2000 non-zero visual words per image, which is significantly more than our learnt 128 or 512 dimensional descriptor.
-
          \textcolor{petr}{
-         We also performed p-val calibration proposed by Gronat et al.~\cite{Gronat13} on e-SVM Fisher vectors.
+         On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the method of~\cite{Gronat13} who report on the similar testing data.
+Our method outperforms~\cite{Gronat13} already for dimension $d=128$ (37.8\%).
+         \\
+         The p-val calibration proposed by Gronat et al.~\cite{Gronat13} was also tested on e-SVM Fisher vectors.
 We found that the calibration did not perform for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128).
 When examining the results, we believe this may be attributed to the fact that Fisher vectors are low dimensional compared to the extremely high-dimensional (d=100,000) bag-of-visual-words representation, which affects the distribution of the classifier scores on the negative test data.
+         \\
+         Finally, we investigate how performs a raw exemplar-SVM without any further calibration both image descriptors .
+We observe that while using raw SVM scores directly without any calibration fails on BOW (as reported in \cite{Gronat13}), it marginally improves the recall for larger $K$ for Fisher vectors as indicated in \ref{tab:recall}.
           %We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors.
@@
          \end{figure}
-         \begin{table}[htb]
+         \begin{table}[b]
             \begin{centering}
@@
 
-         \begin{table}[htb]
+         \begin{table}[t]
             \begin{centering}
@@
                 \textbf{Examples of correctly and incorrectly localized queries for the learnt Fisher vector representation.}
-                Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by the learnt Fisher vector representation \emph{w-norm} method (top) and the standard Fisher vector baseline (bottom) for dimension 128.
+                Each example shows a query image (left) together with correct (green) and incorrect (red) matches from the database obtained by the learnt Fisher vector representation \emph{e-SVM} method (top) and the standard Fisher vector baseline (bottom) for dimension 128.
 Note that the proposed method is able to recognize the place depicted in the query image despite changes in viewpoint, illumination and partial occlusion by other objects (trees, lamps) and buildings.

### 2014-11-13 cvpr15review.tex
edited blue text

@@
 The image database can be further augmented by 3D point clouds~\cite{Klinger13}, automatically reconstructed by large-scale structure from motion (SfM)~\cite{Agarwal-ICCV-2009,Klinger13}, which enables accurate prediction of query image camera position~\cite{Li12,Sattler12}.
-In this work we investigate learning a discriminative representation using the compact Fisher vector descriptors~\cite{Jegou12}.
+     In this work we investigate learning a discriminative place-specific image representation. A similar idea has been recently explored in~\cite{Cao13} 
+    who learn a graph-based discriminative representation for landmark image collections where typically many images are available for each place.
+    In contrast, we focus on street-level images such as Google street-view, which have greater coverage, but typically only one or a small number of images are  available for each place.  
+     We investigate learning a discriminative representation using the compact Fisher vector descriptors~\cite{Jegou12}.
 Fisher vector descriptors have shown excellent place recognition accuracy~\cite{Torii2013}.
@@
    % such that at query time, 
-   \textcolor{petr}{At query time,} given the Fisher vector $\Phi_q$ of an unknown query image, we retrieve the database image depicting the same location by finding the image $j^*$ with the highest score measured by a dot product
+   At query time, given the Fisher vector $\Phi_q$ of an unknown query image, we retrieve the database image depicting the same location by finding the image $j^*$ with the highest score measured by a dot product
    %
@@
          \end{equation}
-
       \textcolor{petr}{%TODO: \emph{we should't speak about calibration, we shoud address not ignoring $b$}\\
-         The intuition is that for L2 normalized query descriptors $\Phi_q$ computing the calibrated score $f(x)$ corresponds to computing the normalized cross-correlation between vectors $\Psi_j$ and $\Phi_q$.
+%      Measuring the similarity between descriptors by their normalized cross-correlation 
+         Note again that for L2 normalized query descriptor $\Phi_q$, evaluating $\Phi_q^T\Psi_j$ in eq.~\eqref{eq:class} corresponds to computing the normalized cross-correlation between $\Phi_q$ and $\Psi_j$.
 This was found to work well in retrieval (see e.g.~\cite{Sivic03}) or matching whitened HOG descriptors \cite{Gharbi12, Hariharan12}, but has not yet been used in conjunction with SVMs.
-         \\
-         Notice that even the new descriptor $\Psi_j$ is obtained by normalization of the learnt hyperplane $w_j$, the bias $b$ form equation~\eqref{eq:decomposed} is not ignored.
+         Note that while the bias term $b$ is not directly used in the construction of $\Psi_j$, the bias affects the learnt optimal $w_j$ as it appears in the SVM objective~\eqref{eq:obj}. 
+         % when learning the optimal SVM hyper-plane $w_j$.           
+%         even the new descriptor $\Psi_j$ is obtained by normalization of the learnt hyperplane $w_j$, the bias $b$ form equation~\eqref{eq:decomposed} is not ignored.
 Indeed, the bias term in convex objective~\eqref{eq:obj} is affecting the learnt the hyperplane.
-         %\\
+%         %\\
          %The proposed re-normalization procedure can be interpreted as a simple form of affine calibration where the uncalibrated SVM score $s(x)=w^T x+b$ is transformed into a calibrated score $f(x)=\alpha s(x)+\beta$, where $\alpha = 1/||w||$ and $\beta = -b\alpha$.
@@
    \subsection{Results}  
-      For each database (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).
+      For both databases (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).
+%  For the Pittsburgh 25k database we also compare results to exemplar SVM learning without the proposed descriptor re-normalization (SVM raw).
 
@@
          The proposed approach can be applied to other descriptors beyond Fisher vectors.
-To demonstrate this we have applied the proposed method to the bag-of-visual-words descriptor and observed improvement from 28.7\% recall@K=1 (vanilla bag-of-visual-words) to 31.8\% recall@K=1 (e-SVM).
-For bag-of-visual-words, the e-SVM with p-value calibration gives comparable results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method very hard to scale-up to database sizes beyond 200k images.
-The results are given in table \ref{tab:recall}.
+To demonstrate this we have applied the proposed method to the bag-of-visual-words descriptor and observed improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
+For bag-of-visual-words,  the e-SVM with p-value calibration of~\cite{Gronat13} (BOW p-val) gives a slightly better results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
+The results are given in table \ref{tab:recall} (top four rows).
         }
@@
          \textcolor{petr}{
-         On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the method of~\cite{Gronat13} who report on the similar testing data.
+         On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the method of~\cite{Gronat13} who report results on similar testing data.
 Our method outperforms~\cite{Gronat13} already for dimension $d=128$ (37.8\%).
-         \\
-         The p-val calibration proposed by Gronat et al.~\cite{Gronat13} was also tested on e-SVM Fisher vectors.
-We found that the calibration did not perform for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128).
+  %       \\
+         We have also tested the p-val calibration of~\cite{Gronat13} on e-SVM Fisher vectors.
+We found that the calibration did not perform well for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128).
 When examining the results, we believe this may be attributed to the fact that Fisher vectors are low dimensional compared to the extremely high-dimensional (d=100,000) bag-of-visual-words representation, which affects the distribution of the classifier scores on the negative test data.
-         \\
-         Finally, we investigate how performs a raw exemplar-SVM without any further calibration both image descriptors .
-We observe that while using raw SVM scores directly without any calibration fails on BOW (as reported in \cite{Gronat13}), it marginally improves the recall for larger $K$ for Fisher vectors as indicated in \ref{tab:recall}.
+%         \\
+         Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration for both image descriptors .
+We observe that while using raw SVM scores directly without any calibration fails for the bag-of-visual-words representation (BOW raw SVM) (as reported in \cite{Gronat13}), it marginally improves recall for larger $K$ for Fisher vectors (68.4\% for FV128 raw SVM compared to 67.7\% for non-learned FV128).
+%         as indicated in \ref{tab:recall} (FV128 raw SVM).
           %We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors.
@@
                   \textcolor{petr}{
-                     in top $K\in\{1,2,5,10,20\}$ retrieved images.
-                     Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions.The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
+                     in the top $K\in\{1,2,5,10,20\}$ retrieved images.
+%                     Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions.
+The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
                   } 
-                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions on both the 25k and 55k Pittsburgh image datasets.
+                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors (FV) across the whole range of $K$  and all dimensions.
+%                   on both the 25k and 55k Pittsburgh image datasets.     
             }
@@
                   } 
-                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions on both the 25k and 55k Pittsburgh image datasets.
+                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions.
+%                   on both the 25k and 55k Pittsburgh image datasets.     
                }

### 2014-11-14 cvpr15review.tex
results: major revision

@@
    \subsection{Results} 
-      For both databases (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).
-%  For the Pittsburgh 25k database we also compare results to exemplar SVM learning without the proposed descriptor re-normalization (SVM raw).
+      \textcolor{petr}{
+         The experiments are performed on two datasets (Pittsburgh 25k and Pittsburgh 55k) on several target Fisher vector dimensions $d\in\{128,512,2048\}$.
+The proposed approach can be also applied to other descriptors beyond Fisher vectors.
+To demonstrate this we have applied the proposed method to the bag-of-visual-words.
+         \\
+         For each method we measure performance using the percentage of correctly recognized queries (Recall) similarly to, e.g.,~\cite{Chen11,Knopp2010,Sattler-BMVC12}.
+The query is correctly localized if at least one of the top $K$ retrieved database images is within $20$ meters from the ground truth position of the query.
+Results are shown for different values of $K$ in tables~\ref{tab:recallBOW},~\ref{tab:recall} and \ref{tab:recall2}.
+For the Pittsburgh 25k we also show results in the form of a curve in figure~\ref{fig:recall}.
+The results clearly demonstrate the benefits of the learnt descriptors with respect to the standard Fisher vectors for all target dimensions and lengths of shortlist $K$.
+The benefits of discriminative learning are specially prominent for low-dimensional compact descriptors ($d=128$).
+Figure~\ref{fig:images} shows examples of place recognition results.
+      }
 
-      We perform experiments on several target Fisher vector dimensions $d\in\{128,512,2048\}$.
+      % For both databases (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).
+
+      % We perform experiments on several target Fisher vector dimensions $d\in\{128,512,2048\}$.
 For each method we measure performance using the percentage of correctly recognized queries (Recall) similarly to, e.g.,~\cite{Chen11,Knopp2010,Sattler-BMVC12}.
@@
 The benefits of discriminative learning are specially prominent for low-dimensional compact descriptors ($d=128$).
-      The proposed method also significantly outperforms the bag-of-visual-words baseline. Figure~\ref{fig:images} shows examples of place recognition results.
+      % The proposed method also significantly outperforms the bag-of-visual-words baseline. Figure~\ref{fig:images} shows examples of place recognition results.
 
-      \paragraph{Applying our learning method to other descriptors.}
+      \paragraph{Bag-of-visual-words}
          \textcolor{petr}{
-         The proposed approach can be applied to other descriptors beyond Fisher vectors.
-To demonstrate this we have applied the proposed method to the bag-of-visual-words descriptor and observed improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
-For bag-of-visual-words,  the e-SVM with p-value calibration of~\cite{Gronat13} (BOW p-val) gives a slightly better results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
-The results are given in table \ref{tab:recall} (top four rows).
+            For bag of visual words image representation we provide three kind of results summarized in table \ref{tab:recallBOW}.
+First, similarly to \cite{Gronat13}, we compare proposed method (e-SVM) to the standard bag-of-visual-words baseline (BOW).
+We observe improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
+Secondly, the results are also confronted to the p-value calibration of \cite{Gronat13}.
+The p-value calibration (BOW p-val) gives marginally better results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
+Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) with no calibration.
+As reported in \cite{Gronat13}, we observe that using these scores directly with no calibration does not perform on BOW.
+However, this method gives surprisingly good results on Fisher vectors.
+Details will be given next.
          }
 
-      \paragraph{Comparison to other methods.}
-         %On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the methods of~\cite{Gronat13} and~\cite{Knopp2010}, who report on the same testing data top $K=1$ recall of 36.5\% and 41.9\%, respectively (results taken from~\cite{Gronat13}).
+         \begin{table}[b]
+            \begin{centering}
+               \include{table25kBOW}
+            \caption{ \textbf{Results on Pittsburgh 25k dataset - BOW.}
+                  The fraction of correctly recognized queries (recall@K)
+                  \textcolor{petr}{
+                     in the top $K\in\{1,2,5,10,20\}$ retrieved images.
+                     % Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions.
+The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
+                  } 
+                  The learnt descriptors by the proposed method (BOW e-SVM) marginally improves over the raw bag-of-visual-words descriptors (BOW) across the whole range of $K$  and all dimensions.
+%                   on both the 25k and 55k Pittsburgh image datasets.     
+            }
+            \label{tab:recallBOW}
+            \end{centering}
+         \end{table}
+
+      \paragraph{Fisher vectors}
+         \begin{table}[b]
+            \begin{centering}
+               \include{table25k}
+            \caption{ \textbf{Results on Pittsburgh 25k dataset.}
+                  The fraction of correctly recognized queries (recall@K)
+                  \textcolor{petr}{
+                     in the top $K\in\{1,2,5,10,20\}$ retrieved images.
+                     % Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions.
+The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
+                  } 
+                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors (FV) across the whole range of $K$  and all dimensions.
+%                   on both the 25k and 55k Pittsburgh image datasets.     
+            }
+            \label{tab:recall}
+            \end{centering}
+         \end{table}
+         %
+         \textcolor{petr}{
+         Table \ref{tab:recall} summarizes the results of proposed method that has been applied on Fisher vectors for several target dimensions $d\in\{128,512,2048\}$.
+The learnt image representation (FV e-SVM) significantly outperforms the Fisher vector baseline (FV).
+The improvements are consistent across different lengths $K$ of the shortlist for all target dimensions of the Fisher vectors.
+         Figure \ref{fig:recall} shows the results in a form of curve and it clearly demonstrates the benefits of the learnt descriptors.
+For comprehensiveness the figure also shows the BOW baseline curve from table \ref{tab:recallBOW} shown in black.
+         \\
+         The p-val calibration of~\cite{Gronat13} has been tested on e-SVM Fisher vectors.
+We found that the calibration did not perform well for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128).
+When examining the results, we believe this may be attributed to the fact that Fisher vectors are low dimensional compared to the extremely high-dimensional (d=100,000) bag-of-visual-words representation, which affects the distribution of the classifier scores on the negative test data.
+         \\
+         Next, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration for both image descriptors .
+We observe that while using raw SVM scores directly without any calibration fails for the bag-of-visual-words representation (BOW raw SVM) (as reported in \cite{Gronat13}), it marginally improves recall for larger $K$ for Fisher vectors (68.4\% for FV128 raw SVM compared to 67.7\% for non-learned FV128).
+         \\
+         Finally, we performed experiments on the Pittsburgh 55k dataset.
+Similarly to the former dataset, the results summarized in table \ref{tab:recall2} show consistent improvement of the proposed method (FV e-SVM) over the Fisher vector baseline (FV) across all target dimensions.
+The benefits of the proposed method in terms of memory efficiency will be discussed next.
+         }
+         %
+         \begin{table}[t]
+            \begin{centering}
+               \include{table55k}
+               \caption{ \textbf{Results on Pittsburgh 55k dataset - FV.}
+                  The fraction of correctly recognized queries (recall@K)
+                  \textcolor{petr}{
+                  in top $K\in\{1,2,5,10,20\}$ retrieved images.
+                  The proposed method (\emph{e-SVM}) has been applied to Fisher vectors compressed to different dimensions.
+                  } 
+                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions.
+%                   on both the 25k and 55k Pittsburgh image datasets.     
+               }
+            \label{tab:recall2}
+            \end{centering}
+         \end{table}
+
+      % \paragraph{Applying our learning method to other descriptors.}
+      %   \textcolor{petr}{ 
+      %    The proposed approach can be applied to other descriptors beyond Fisher vectors.
+To demonstrate this we have applied the proposed method to the bag-of-visual-words descriptor and observed improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
+      %    For bag-of-visual-words,  the e-SVM with p-value calibration of~\cite{Gronat13} (BOW p-val) gives a slightly better results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
+The results are given in table \ref{tab:recall} (top four rows).
+      %   }
+
+%       \paragraph{Comparison to other methods.}
+%          %On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the methods of~\cite{Gronat13} and~\cite{Knopp2010}, who report on the same testing data top $K=1$ recall of 36.5\% and 41.9\%, respectively (results taken from~\cite{Gronat13}).
 Our method outperforms~\cite{Knopp2010} already for dimension $d=128$ (37.8\%) and~\cite{Gronat13} for dimension $d=512$ (47.6\%).
 Furthermore, note that~\cite{Gronat13,Knopp2010} are based on a bag-of-visual-words representation, which typically needs to store between 1000-2000 non-zero visual words per image, which is significantly more than our learnt 128 or 512 dimensional descriptor.
-         \textcolor{petr}{
-         On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the method of~\cite{Gronat13} who report results on similar testing data.
+%          \textcolor{petr}{
+%          On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the method of~\cite{Gronat13} who report results on similar testing data.
 Our method outperforms~\cite{Gronat13} already for dimension $d=128$ (37.8\%).
-  %       \\
-         We have also tested the p-val calibration of~\cite{Gronat13} on e-SVM Fisher vectors.
+%   %       \\
+%          We have also tested the p-val calibration of~\cite{Gronat13} on e-SVM Fisher vectors.
 We found that the calibration did not perform well for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128).
 When examining the results, we believe this may be attributed to the fact that Fisher vectors are low dimensional compared to the extremely high-dimensional (d=100,000) bag-of-visual-words representation, which affects the distribution of the classifier scores on the negative test data.
-%         \\
-         Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration for both image descriptors .
+% %         \\
+%          Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration for both image descriptors .
 We observe that while using raw SVM scores directly without any calibration fails for the bag-of-visual-words representation (BOW raw SVM) (as reported in \cite{Gronat13}), it marginally improves recall for larger $K$ for Fisher vectors (68.4\% for FV128 raw SVM compared to 67.7\% for non-learned FV128).
-%         as indicated in \ref{tab:recall} (FV128 raw SVM).
-          %We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors.
+% %         as indicated in \ref{tab:recall} (FV128 raw SVM).
+%           %We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors.
 The results show that our method significantly outperforms the p-value calibration (37.8\% recall@1 vs.
@@
 Similar gains are observed for other FV dimensions.
-        }
+%         }
       \paragraph{Memory complexity analysis.}
@@
          \end{figure}
-         \begin{table}[b]
-            \begin{centering}
-               \include{table25k}
-            \caption{ \textbf{Results on Pittsburgh 25k dataset.}
-                  The fraction of correctly recognized queries (recall@K)
-                  \textcolor{petr}{
-                     in the top $K\in\{1,2,5,10,20\}$ retrieved images.
-%                     Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions.
-The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
-                  } 
-                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors (FV) across the whole range of $K$  and all dimensions.
-%                   on both the 25k and 55k Pittsburgh image datasets.     
-            }
-            \label{tab:recall}
-            \end{centering}
-         \end{table}
-
-         \begin{table}[t]
-            \begin{centering}
-               \include{table55k}
-               \caption{ \textbf{Results on Pittsburgh 55k dataset.}
-                  The fraction of correctly recognized queries (recall@K)
-                  \textcolor{petr}{
-                  in top $K\in\{1,2,5,10,20\}$ retrieved images.
-                  The proposed method (\emph{e-SVM}) has been applied to Fisher vectors compressed to different dimensions.
-                  } 
-                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions.
-%                   on both the 25k and 55k Pittsburgh image datasets.     
-               }
-            \label{tab:recall2}
-            \end{centering}
-         \end{table}
+         %
+         %
          %

### 2014-11-14 cvpr15review.tex
results section

@@
 \begin{abstract}
+   \noindent
    The goal of this work is to localize a query photograph by finding other images depicting the same place in a large geotagged image database.
@@
 Secondly, we analyze the exemplar support vector machine objective and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data.
-Finally, based on this analysis we demonstrate that the learnt and re-normalized descriptor could be directly used for matching, thus avoiding the need for expensive and tedious calibration typically needed for exemplar support vector machine methods.
+Finally, based on this analysis, we demonstrate that the learnt and re-normalized descriptor could be directly used for matching, thus avoiding the need for expensive and tedious calibration typically needed for exemplar support vector machine methods.
 Place recognition results are shown on two image datasets of Google street-view images from Pittsburgh  and demonstrate the learnt representation consistently improves over the standard Fisher vector descriptors at different target dimensions.
@@
 \section{Introduction}
-
+\noindent
 The goal of this work is to localize a query image by matching to a large database of geotagged street-level imagery.
@@
 
-         In detail, for $w=w^{\perp}+w^{||}$ the objective~(\ref{eq:obj}) can be written as
+         In detail, for $w=w^{\perp}+w^{||}$, the objective~(\ref{eq:obj}) can be written as
             %
@@
 
-      \paragraph{Bag-of-visual-words}
+      \paragraph{Bag-of-visual-words.}
          \textcolor{petr}{
             For bag of visual words image representation we provide three kind of results summarized in table \ref{tab:recallBOW}.
-First, similarly to \cite{Gronat13}, we compare proposed method (e-SVM) to the standard bag-of-visual-words baseline (BOW).
+First, similarly to \cite{Gronat13}, we compare the proposed method (e-SVM) to the standard bag-of-visual-words baseline (BOW).
 We observe improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
 Secondly, the results are also confronted to the p-value calibration of \cite{Gronat13}.
-The p-value calibration (BOW p-val) gives marginally better results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
+The p-value calibration (BOW p-val) gives marginally better results (33.0\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
 Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) with no calibration.
-As reported in \cite{Gronat13}, we observe that using these scores directly with no calibration does not perform on BOW.
-However, this method gives surprisingly good results on Fisher vectors.
-Details will be given next.
+As reported in \cite{Gronat13}, we observe that using raw SVM scores directly with no calibration does not perform on BOW.
+However, this method gives satisfiable good results on Fisher vectors.
+Details are be given next.
          }
@@
                   } 
-                  The learnt descriptors by the proposed method (BOW e-SVM) marginally improves over the raw bag-of-visual-words descriptors (BOW) across the whole range of $K$  and all dimensions.
+                  The learnt descriptors by the proposed method (BOW e-SVM) marginally improves over the raw bag-of-visual-words descriptors (BOW).
 %                   on both the 25k and 55k Pittsburgh image datasets.     
@@
 
-      \paragraph{Fisher vectors}
+      \paragraph{Fisher vectors.}
          \begin{table}[b]
@@
          Figure \ref{fig:recall} shows the results in a form of curve and it clearly demonstrates the benefits of the learnt descriptors.
-For comprehensiveness the figure also shows the BOW baseline curve from table \ref{tab:recallBOW} shown in black.
+For comprehensiveness the figure also shows the BOW baseline curve taken from table \ref{tab:recallBOW} shown in black.
          \\
-         The p-val calibration of~\cite{Gronat13} has been tested on e-SVM Fisher vectors.
+         The p-val calibration of~\cite{Gronat13} has been also tested on e-SVM Fisher vectors.
 We found that the calibration did not perform well for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128).
@@
          \\
-         Next, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration for both image descriptors .
-We observe that while using raw SVM scores directly without any calibration fails for the bag-of-visual-words representation (BOW raw SVM) (as reported in \cite{Gronat13}), it marginally improves recall for larger $K$ for Fisher vectors (68.4\% for FV128 raw SVM compared to 67.7\% for non-learned FV128).
+         Next, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration on Fisher vectors.
+We observe that while using raw SVM scores directly without any calibration fails for the bag-of-visual-words representation (BOW raw SVM, talbe~\ref{tab:recallBOW}), as reported in \cite{Gronat13}, it marginally improves the recall for larger $K$ for Fisher vectors (68.4\% for FV128 raw SVM compared to 67.7\% for non-learned FV128).
          \\
-         Finally, we performed experiments on the Pittsburgh 55k dataset.
+         Finally, we performed experiments on the larger Pittsburgh 55k dataset.
 Similarly to the former dataset, the results summarized in table \ref{tab:recall2} show consistent improvement of the proposed method (FV e-SVM) over the Fisher vector baseline (FV) across all target dimensions.

### 2014-11-14 cvpr15review.tex
comments by Tomas fixed

@@
       Details are given next.
-
+            %
+            \begin{figure}[t]
+               \begin{center}
+                  \subfigure[$C_2>0$ ]{
+                     \centering
+                     \includegraphics[width=0.45\linewidth]{imgs/figSVM01tight}
+                  }
+                  %        $C_2 \rightarrow 0$
+                  \subfigure[$C_2 \rightarrow 0$]{
+                     \centering
+                     \includegraphics[width=0.45\linewidth]{imgs/figSVM02tight}
+                  }
+                  \caption{
+                     {\bf An illustration of the effect of decreasing parameter $C_2$ in the exemplar support vector machine objective.} 
+                     The positive exemplar $\Phi_j^+$ is shown in green.
+The negative data points are shown in red.
+All training data is L2 normalized to lie on a hyper-sphere.
+(a) For $C_2>0$, the normal $w_j$ of the optimal hyper-plane moves away from the direction given by the positive example $\Phi^+$ in a manner that reduces the loss on the negative data.
+(b) As the parameter $C_2$ decreases the learnt $w_j$ becomes parallel to the positive training example $\Phi_j^+$ and its magnitude $||w_j||$ goes to 0.
+                  }
+                  \label{fig:C2effect}
+               \end{center}
+            \end{figure}
+            %
       \paragraph{Case I: $C_2\rightarrow 0$.}
@@
 Explicitly writing the hinge-loss $h(x) = \max(1-x,0)$ in the last term of~\eqref{eq:decomposed}, we see that $w$ will move in the direction that reduces $\sum_{\Phi\in \mathcal N}\max \left(1+w^T \Phi + b ,0 \right)$, i.e.\ that reduces the dot product $w^T \Phi$ on the negative examples that are active (support vectors).
-            %
-            \begin{figure}[t]
-               \begin{center}
-                  \subfigure[$C_2>0$ ]{
-                     \centering
-                     \includegraphics[width=0.45\linewidth]{imgs/figSVM01tight}
-                  }
-                  %        $C_2 \rightarrow 0$
-                  \subfigure[$C_2 \rightarrow 0$]{
-                     \centering
-                     \includegraphics[width=0.45\linewidth]{imgs/figSVM02tight}
-                  }
-                  \caption{
-                     {\bf An illustration of the effect of decreasing parameter $C_2$ in the exemplar support vector machine objective.} 
-                     The positive exemplar $\Phi_j^+$ is shown in green.
-The negative data points are shown in red.
-All training data is L2 normalized to lie on a hyper-sphere.
-(a) For $C_2>0$, the normal $w_j$ of the optimal hyper-plane moves away from the direction given by the positive example $\Phi^+$ in a manner that reduces the loss on the negative data.
-(b) As the parameter $C_2$ decreases the learnt $w_j$ becomes parallel to the positive training example $\Phi_j^+$ and its magnitude $||w_j||$ goes to 0.
-                  }
-                  \label{fig:C2effect}
-               \end{center}
-            \end{figure}
 
@@
 %      Measuring the similarity between descriptors by their normalized cross-correlation 
-         Note again that for L2 normalized query descriptor $\Phi_q$, evaluating $\Phi_q^T\Psi_j$ in eq.~\eqref{eq:class} corresponds to computing the normalized cross-correlation between $\Phi_q$ and $\Psi_j$.
+         Note again that for L2 normalized query descriptor $\Phi_q$, evaluating $\Phi_q^T\Psi_j$ in eq.~\eqref{eq:class} corresponds to computing the~normalized cross-correlation between $\Phi_q$ and $\Psi_j$.
 This was found to work well in retrieval (see e.g.~\cite{Sivic03}) or matching whitened HOG descriptors \cite{Gharbi12, Hariharan12}, but has not yet been used in conjunction with SVMs.
@@
 \label{sec:exp}
-   In this section we first describe the experimental set-up, then we give implementation details, and finally report results of the proposed approach on two datasets where we compare performance with raw Fisher vector matching and several baselines methods.
+   In this section we first describe the experimental set-up, then give implementation details, and finally report results of the proposed approach on two datasets where we compare performance with raw Fisher vector matching and several baselines methods.
 
@@
 The proposed approach can be also applied to other descriptors beyond Fisher vectors.
-To demonstrate this we have applied the proposed method to the bag-of-visual-words.
+To demonstrate this we have applied the proposed method to the bag-of-visual-words (BOW).
          \\
@@
 However, this method gives satisfiable good results on Fisher vectors.
-Details are be given next.
+Details are given next.
          }

### 2014-11-14 cvpr15review.tex
small edits result section

@@
          \textcolor{petr}{
-            For bag of visual words image representation we provide three kind of results summarized in table \ref{tab:recallBOW}.
-First, similarly to \cite{Gronat13}, we compare the proposed method (e-SVM) to the standard bag-of-visual-words baseline (BOW).
-We observe improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
-Secondly, the results are also confronted to the p-value calibration of \cite{Gronat13}.
-The p-value calibration (BOW p-val) gives marginally better results (33.0\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
+            For the bag-of-visual-words image representation we provide three kinds of results summarized in table \ref{tab:recallBOW}.
+First, we compare the proposed method (e-SVM) to the standard bag-of-visual-words baseline (BOW).
+We observe an improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
+Secondly, the results are also compared to the p-value calibration from~\cite{Gronat13}.
+The p-value calibration (BOW p-val) gives marginally better results for small short lists (33.0\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
 Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) with no calibration.
-As reported in \cite{Gronat13}, we observe that using raw SVM scores directly with no calibration does not perform on BOW.
-However, this method gives satisfiable good results on Fisher vectors.
+As reported in \cite{Gronat13}, we observe that using raw SVM scores directly with no calibration does not perform well for the bag-of-visual-words representation.
+%We describe results on Fisher vectors next.
+%However, this method gives satisfiable good results on Fisher vectors.
 Details are given next.
@@
                   } 
-                  The learnt descriptors by the proposed method (BOW e-SVM) marginally improves over the raw bag-of-visual-words descriptors (BOW).
+                  The learnt descriptors by the proposed method (BOW e-SVM) marginally improve over the raw bag-of-visual-words descriptors (BOW).
 %                   on both the 25k and 55k Pittsburgh image datasets.     
@@
          \textcolor{petr}{
-         Table \ref{tab:recall} summarizes the results of proposed method that has been applied on Fisher vectors for several target dimensions $d\in\{128,512,2048\}$.
+         Table \ref{tab:recall} summarizes results of the proposed method applied to Fisher vectors for several target dimensions $d\in\{128,512,2048\}$.
 The learnt image representation (FV e-SVM) significantly outperforms the Fisher vector baseline (FV).
 The improvements are consistent across different lengths $K$ of the shortlist for all target dimensions of the Fisher vectors.
-         Figure \ref{fig:recall} shows the results in a form of curve and it clearly demonstrates the benefits of the learnt descriptors.
-For comprehensiveness the figure also shows the BOW baseline curve taken from table \ref{tab:recallBOW} shown in black.
+         Figure \ref{fig:recall} shows the results in the form of a curve and it clearly demonstrates the benefits of the learnt descriptors. 
+%         For completeness the figure also shows the BOW baseline curve taken from table \ref{tab:recallBOW} shown in black.
          \\
-         The p-val calibration of~\cite{Gronat13} has been also tested on e-SVM Fisher vectors.
+         We have also tested on the learnt e-SVM Fisher vectors the p-val calibration of~\cite{Gronat13}.
 We found that the calibration did not perform well for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128).
@@
          \\
-         Next, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration on Fisher vectors.
+         Next, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration.
 We observe that while using raw SVM scores directly without any calibration fails for the bag-of-visual-words representation (BOW raw SVM, talbe~\ref{tab:recallBOW}), as reported in \cite{Gronat13}, it marginally improves the recall for larger $K$ for Fisher vectors (68.4\% for FV128 raw SVM compared to 67.7\% for non-learned FV128).
@@
          Finally, we performed experiments on the larger Pittsburgh 55k dataset.
-Similarly to the former dataset, the results summarized in table \ref{tab:recall2} show consistent improvement of the proposed method (FV e-SVM) over the Fisher vector baseline (FV) across all target dimensions.
-The benefits of the proposed method in terms of memory efficiency will be discussed next.
+The results are summarized in table \ref{tab:recall2} and show a consistent improvement of the proposed method (FV e-SVM) over the Fisher vector baseline (FV) across all target dimensions.
+%         The benefits of the proposed method in terms of memory efficiency will be discussed next.
          }
@@
          \end{table}
+
+	% Additional results are given in supplementary material.
 

### 2014-11-14 cvpr15review.tex
final commit before submission

@@
 \usepackage{hyphenat}
-
+\renewcommand{\baselinestretch}{0.986}
 % Include other packages here, before hyperref.
@@
 The contributions of this work are three fold.
-First, we learn a {\em discriminative} yet {\em compact} descriptor of each image in the database.
+First, we learn a {\em discriminative}, yet {\em compact}, descriptor of each image in the database.
 This is achieved by applying exemplar support vector machine (e-SVM) learning to compact Fisher vector descriptors extracted from database images.
 Secondly, we analyze the exemplar support vector machine objective and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data.
-Finally, based on this analysis, we demonstrate that the learnt and re-normalized descriptor could be directly used for matching, thus avoiding the need for expensive and tedious calibration typically needed for exemplar support vector machine methods.
+Finally, based on this analysis, we demonstrate that the learnt and re-normalized descriptor can be directly used for matching, thus avoiding the need for expensive and tedious calibration typically needed for exemplar support vector machine methods.
 Place recognition results are shown on two image datasets of Google street-view images from Pittsburgh  and demonstrate the learnt representation consistently improves over the standard Fisher vector descriptors at different target dimensions.
@@
 It is hard to distinguish different places, e.g.\ streets in a city, from each other.
-The imaged appearance of a place can change drastically due to factors such as  viewpoint, illumination or even changes over time.
+The image appearance of a place can change drastically due to factors such as  viewpoint, illumination or even changes over time.
    %
@@
 First, the learnt place specific representation is not compact, which prohibits its application to planet-scale street-level collections that are now becoming available~\cite{Klinger13}.
-Second, the per-exemplar classifiers require careful and time-consuming calibration.
+Secondly, the per-exemplar classifiers require careful and time-consuming calibration.
 
    In this work we address both these issues. 
-First, we apply the exemplar SVM training to compact Fisher vector~\cite{Jegou2011,Perronnin2010} image descriptors, which results in a {\em discriminative} yet {\em compact} representation of each image in the database.
-Second, to avoid the expensive classifier calibration, we analyze the exemplar SVM cost and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data.
+   First, we apply the exemplar SVM training to compact Fisher vector~\cite{Jegou2011,Perronnin2010} image descriptors, which results in a {\em discriminative}, yet {\em compact}, representation of each image in the database.
+Secondly, to avoid the expensive classifier calibration, we analyze the exemplar SVM cost and show that the learnt hyperplane can be interpreted as a new descriptor that replaces the original positive example and is re-weighted to increase its separation from the negative data.
 As a result of this analysis, we demonstrate that after an appropriate normalization of the new re-weighted descriptor no further calibration is necessary.
 We show improved results on place recognition using learnt compact Fisher vector descriptors~\cite{Jegou2011} of different dimensionality.
-%-------------------------------------------------------------------------
+
 \section{Related work} 
    \label{sec:related}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 However, the raw extracted Fisher vectors are typically high-dimensional, e.g.\ with 32,768 non-sparse dimensions, which is impractical for large-scale visual recognition and indexing applications.
-Hence, their dimensionality is often reduced by principal component analysis (PCA) and further quantized for efficient indexing using, e.g.\ a product quantizer~\cite{Jegou12}.
+Hence, their dimensionality is often reduced by principal component analysis (PCA) and further quantized for efficient indexing using e.g.\ a product quantizer~\cite{Jegou12}.
 Other recent work has demonstrated improved performance in a face recognition application by finding discriminative projection using a large amount of training face data~\cite{Simonyan2013}.
@@
 Secondly, we demonstrate that after an appropriate normalization of the new re-weighted descriptor no further calibration is necessary.
-Finally, we apply e-SVM training to compact Fisher vector descriptors for large-scale place recognition resulting in a {\em discriminative} yet {\em compact} representation of each image in the database.
+Finally, we apply e-SVM training to compact Fisher vector descriptors for large-scale place recognition resulting in a {\em discriminative}, yet {\em compact}, representation of each image in the database.
 Place recognition results are shown on a dataset of 25k images of Pittsburgh and demonstrate the learnt representation consistently improves over the standard Fisher vector descriptors at different target dimensions.
@@
 Inspired by~\cite{Gronat13}, we investigate applying the exemplar support vector machine (e-SVM)~\cite{Malisiewicz11} for this task.
-e-SVM learns a linear classifier $w_j^T\Phi+b_j$ given the descriptor $\Phi_j^+$ of place $j$ as a single positive example (with target label +1) and a large number of negative descriptors $\mathcal N_j$ from other places in the database (with target labels -1).
+e-SVM learns a linear classifier $w_j^T\Phi+b_j$ given the descriptor $\Phi_j^+$ of place $j$ as a single positive training example (with target label +1) and a large number of negative descriptors $\mathcal N_j$ from other places in the database (with target labels -1).
 The intuition of the exemplar SVM training~\cite{Malisiewicz11} is that the learnt weight vector $w_j$ will give a higher weight to the dimensions of the descriptor that are discriminative and will down-weight dimensions that are non-discriminative with respect to the negative training data collected from other far-away places.
@@
       In this section, we analyze the exemplar SVM objective~(\ref{eq:obj}) and show the learnt and {\em re-normalized} weight vector $w_j$ can be interpreted as a new descriptor $\Psi_j$ that replaces the original positive training descriptor $\Phi^+_j$.
-In particular, we show first that when the weight $C_2$ of the negative data in objective~(\ref{eq:obj}) goes to zero and the learnt $\Psi_j$ is identical to the original positive training data point $\Phi_j^+$.
-Second, when $C_2>0$, the learnt $\Psi_j$ moves away from the positive $\Phi_j^+$ to increase its separation from the negative data.
+In particular, we show first that when the weight $C_2$ of the negative data in objective~(\ref{eq:obj}) goes to zero the learnt $\Psi_j$ is identical to the original positive training data point $\Phi_j^+$.
+Second, when $C_2>0$, the learnt vector $\Psi_j$ moves away from the positive vector  $\Phi_j^+$ to increase its separation from the negative data.
       Details are given next.
@@
                \centering
-                     \includegraphics[width=0.45\linewidth]{imgs/figSVM01tight}
+               \includegraphics[trim = 4mm 0mm 7mm 3mm, clip=true, width=0.47\linewidth]{imgs/figSVM01tight}
             }
@@
                \centering
-                     \includegraphics[width=0.45\linewidth]{imgs/figSVM02tight}
+               \includegraphics[trim = 3mm 0mm 8mm 3mm, clip=true, width=0.47\linewidth]{imgs/figSVM02tight}
             }
@@
 Explicitly writing the hinge-loss $h(x) = \max(1-x,0)$ in the last term of~\eqref{eq:decomposed}, we see that $w$ will move in the direction that reduces $\sum_{\Phi\in \mathcal N}\max \left(1+w^T \Phi + b ,0 \right)$, i.e.\ that reduces the dot product $w^T \Phi$ on the negative examples that are active (support vectors).
+         %
 
@@
 As we wish to measure the similarity between descriptors by (the cosine of) their angle given by equation \eqref{eq:class}, additional normalization of the learnt $w$ is necessary.
-Hence we define the new descriptor $\Psi_j$ as the normalized hyperplane normal $w_j$
+Hence we define the new descriptor $\Psi_j$ as the normalized hyperplane normal~$w_j$
       %
@@
       \end{equation}
-      \textcolor{petr}{%TODO: \emph{we should't speak about calibration, we shoud address not ignoring $b$}\\
-%      Measuring the similarity between descriptors by their normalized cross-correlation 
+
       Note again that for L2 normalized query descriptor $\Phi_q$, evaluating $\Phi_q^T\Psi_j$ in eq.~\eqref{eq:class} corresponds to computing the~normalized cross-correlation between $\Phi_q$ and $\Psi_j$.
@@
       Note that while the bias term $b$ is not directly used in the construction of $\Psi_j$, the bias affects the learnt optimal $w_j$ as it appears in the SVM objective~\eqref{eq:obj}.
-         % when learning the optimal SVM hyper-plane $w_j$.           
-%         even the new descriptor $\Psi_j$ is obtained by normalization of the learnt hyperplane $w_j$, the bias $b$ form equation~\eqref{eq:decomposed} is not ignored.
-Indeed, the bias term in convex objective~\eqref{eq:obj} is affecting the learnt the hyperplane.
-%         %\\
-         %The proposed re-normalization procedure can be interpreted as a simple form of affine calibration where the uncalibrated SVM score $s(x)=w^T x+b$ is transformed into a calibrated score $f(x)=\alpha s(x)+\beta$, where $\alpha = 1/||w||$ and $\beta = -b\alpha$.
-Note that the bias term b is not ignored but used to compute $f(x)$.
-The intuition is that for L2 normalized descriptors x computing the calibrated score $f(x)$ corresponds to computing the normalized cross-correlation between vectors w and x.
-This was found to work well in retrieval (see e.g.
-Sivic and Zisserman, ICCV 2003 [32]) or matching whitened HOG descriptors [11,13] (see e.g.
-[Doersch et al., Mid-Level Visual Element Discovery as discriminative Mode Seeking, NIPS 2013]), but has not yet been used in conjunction with SVMs as done in this work.
-Note also that the affine calibration can be computed offline and does not need any additional computation or storage at query time compared to the p-value calibration of Gronat et al.
-[12].
-      }
 
@@
          \centering
-         \includegraphics[width=\linewidth]{imgs/plotPitt25kSURF}    
+         \includegraphics[trim = 7mm 0mm 12mm 6mm, clip=true, width=1.0\linewidth]{imgs/plotPitt25kSURF}    
          \caption{
@@
 the number of top $K$ retrieved database images for different Fisher vector dimensions.
-The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions.
+The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$ and all~dimensions.
          }
@@
    \subsection{Results} 
-      \textcolor{petr}{
       The experiments are performed on two datasets (Pittsburgh 25k and Pittsburgh 55k) on several target Fisher vector dimensions $d\in\{128,512,2048\}$.
@@
 To demonstrate this we have applied the proposed method to the bag-of-visual-words (BOW).
-         \\
+
       For each method we measure performance using the percentage of correctly recognized queries (Recall) similarly to, e.g.,~\cite{Chen11,Knopp2010,Sattler-BMVC12}.
@@
 Figure~\ref{fig:images} shows examples of place recognition results.
-      }
-
-      % For both databases (Pittsburgh 25k and Pittsburgh 55k) we compare results of our method (FV e-SVM) to two baselines: standard bag-of-visual-words baseline (BOW) and raw Fisher vector matching without learning (FV).
-
-      % We perform experiments on several target Fisher vector dimensions $d\in\{128,512,2048\}$.
-For each method we measure performance using the percentage of correctly recognized queries (Recall) similarly to, e.g.,~\cite{Chen11,Knopp2010,Sattler-BMVC12}.
-The query is correctly localized if at least one of the top $K$ retrieved database images is within $20$ meters from the ground truth position of the query.
-Results are shown for different values of $K$ in tables~\ref{tab:recall} and \ref{tab:recall2}.
-For the Pittsburgh 25k we also show results in the form of a curve in figure~\ref{fig:recall}.
-The results clearly demonstrate the benefits of the learnt descriptors with respect to the standard Fisher vectors for all target dimensions and lengths of shortlist $K$.
-The benefits of discriminative learning are specially prominent for low-dimensional compact descriptors ($d=128$).
-      % The proposed method also significantly outperforms the bag-of-visual-words baseline. Figure~\ref{fig:images} shows examples of place recognition results.
-
-      \paragraph{Bag-of-visual-words.}
-         \textcolor{petr}{
-            For the bag-of-visual-words image representation we provide three kinds of results summarized in table \ref{tab:recallBOW}.
-First, we compare the proposed method (e-SVM) to the standard bag-of-visual-words baseline (BOW).
-We observe an improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
-Secondly, the results are also compared to the p-value calibration from~\cite{Gronat13}.
-The p-value calibration (BOW p-val) gives marginally better results for small short lists (33.0\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
-Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) with no calibration.
-As reported in \cite{Gronat13}, we observe that using raw SVM scores directly with no calibration does not perform well for the bag-of-visual-words representation.
-%We describe results on Fisher vectors next.
-%However, this method gives satisfiable good results on Fisher vectors.
-Details are given next.
-         }
-
-         \begin{table}[b]
-            \begin{centering}
-               \include{table25kBOW}
-            \caption{ \textbf{Results on Pittsburgh 25k dataset - BOW.}
-                  The fraction of correctly recognized queries (recall@K)
-                  \textcolor{petr}{
-                     in the top $K\in\{1,2,5,10,20\}$ retrieved images.
-                     % Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions.
-The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
-                  } 
-                  The learnt descriptors by the proposed method (BOW e-SVM) marginally improve over the raw bag-of-visual-words descriptors (BOW).
-%                   on both the 25k and 55k Pittsburgh image datasets.     
-            }
-            \label{tab:recallBOW}
-            \end{centering}
-         \end{table}
 
@@
                \include{table25k}
-            \caption{ \textbf{Results on Pittsburgh 25k dataset.}
+               \caption{ \textbf{Results on Pittsburgh 25k dataset - Fisher vectors.}
                   The fraction of correctly recognized queries (recall@K)
-                  \textcolor{petr}{
                      in the top $K\in\{1,2,5,10,20\}$ retrieved images.
@@
 The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
-                  } 
                      The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors (FV) across the whole range of $K$  and all dimensions.
@@
          %
-         \textcolor{petr}{
          Table \ref{tab:recall} summarizes results of the proposed method applied to Fisher vectors for several target dimensions $d\in\{128,512,2048\}$.
@@
 The results are summarized in table \ref{tab:recall2} and show a consistent improvement of the proposed method (FV e-SVM) over the Fisher vector baseline (FV) across all target dimensions.
-%         The benefits of the proposed method in terms of memory efficiency will be discussed next.
-         }
-         %
-         \begin{table}[t]
-            \begin{centering}
-               \include{table55k}
-               \caption{ \textbf{Results on Pittsburgh 55k dataset - FV.}
-                  The fraction of correctly recognized queries (recall@K)
-                  \textcolor{petr}{
-                  in top $K\in\{1,2,5,10,20\}$ retrieved images.
-                  The proposed method (\emph{e-SVM}) has been applied to Fisher vectors compressed to different dimensions.
-                  } 
-                  The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions.
-%                   on both the 25k and 55k Pittsburgh image datasets.     
-               }
-            \label{tab:recall2}
-            \end{centering}
-         \end{table}
+         %The benefits of the proposed method in terms of memory efficiency will be discussed next.
 
@@
 
-      % \paragraph{Applying our learning method to other descriptors.}
-      %   \textcolor{petr}{ 
-      %    The proposed approach can be applied to other descriptors beyond Fisher vectors.
-To demonstrate this we have applied the proposed method to the bag-of-visual-words descriptor and observed improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
-      %    For bag-of-visual-words,  the e-SVM with p-value calibration of~\cite{Gronat13} (BOW p-val) gives a slightly better results (33.6\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
-The results are given in table \ref{tab:recall} (top four rows).
-      %   }
-
-%       \paragraph{Comparison to other methods.}
-%          %On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the methods of~\cite{Gronat13} and~\cite{Knopp2010}, who report on the same testing data top $K=1$ recall of 36.5\% and 41.9\%, respectively (results taken from~\cite{Gronat13}).
-Our method outperforms~\cite{Knopp2010} already for dimension $d=128$ (37.8\%) and~\cite{Gronat13} for dimension $d=512$ (47.6\%).
-Furthermore, note that~\cite{Gronat13,Knopp2010} are based on a bag-of-visual-words representation, which typically needs to store between 1000-2000 non-zero visual words per image, which is significantly more than our learnt 128 or 512 dimensional descriptor.
-%          \textcolor{petr}{
-%          On the Pittsburgh 25k database, we compare performance of our learnt discriminative descriptors to the method of~\cite{Gronat13} who report results on similar testing data.
-Our method outperforms~\cite{Gronat13} already for dimension $d=128$ (37.8\%).
-%   %       \\
-%          We have also tested the p-val calibration of~\cite{Gronat13} on e-SVM Fisher vectors.
-We found that the calibration did not perform well for the learnt Fisher vector classifiers (top 1 recall of 25.3\% compared to baseline performance of 33.6\% for dimension 128).
-When examining the results, we believe this may be attributed to the fact that Fisher vectors are low dimensional compared to the extremely high-dimensional (d=100,000) bag-of-visual-words representation, which affects the distribution of the classifier scores on the negative test data.
-% %         \\
-%          Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) without any further calibration for both image descriptors .
-We observe that while using raw SVM scores directly without any calibration fails for the bag-of-visual-words representation (BOW raw SVM) (as reported in \cite{Gronat13}), it marginally improves recall for larger $K$ for Fisher vectors (68.4\% for FV128 raw SVM compared to 67.7\% for non-learned FV128).
-% %         as indicated in \ref{tab:recall} (FV128 raw SVM).
-%           %We have compared the proposed method with the p-value calibration of (Gronat et al.[12]) applied to Fisher vectors.
-The results show that our method significantly outperforms the p-value calibration (37.8\% recall@1 vs.
-32.3\% recall@1; 56.9\%recall@5 vs.
-50.0\% recall@5) for the Fisher vector of dimension 128.
-Similar gains are observed for other FV dimensions.
-%         }
       \paragraph{Memory complexity analysis.}
@@
             \centering
-            \includegraphics[width=1.0\linewidth]{imgs/FVmemory}    
+            \includegraphics[trim = 7mm 0mm 12mm 6mm, clip=true, width=1.0\linewidth]{imgs/FVmemory}    
             \caption{
@@
          \end{figure}
+
+      \paragraph{Bag-of-visual-words.}
+            For the bag-of-visual-words image representation we provide three kinds of results summarized in table \ref{tab:recallBOW}.
+First, we compare the proposed method (e-SVM) to the standard bag-of-visual-words baseline (BOW).
+We observe an improvement from 28.7\% recall@K=1 (BOW) to 31.8\% recall@K=1 (BOW e-SVM).
+Secondly, the results are also compared to the p-value calibration from~\cite{Gronat13}.
+The p-value calibration (BOW p-val) gives marginally better results for small short lists (33.0\% recall@K=1) but at an increased training cost and a significantly higher required memory footprint at query time, which makes the method hard to scale-up to database sizes beyond 200k images.
+Finally, we investigate the performance of a raw exemplar-SVM (raw e-SVM) with no calibration.
+As reported in \cite{Gronat13}, we observe that using raw SVM scores directly with no calibration does not perform well for the bag-of-visual-words representation.
+%We describe results on Fisher vectors next.
+%However, this method gives satisfiable good results on Fisher vectors.
+Details are given next.
             %
+            \begin{table}[t]
+               \begin{centering}
+                  \include{table25kBOW}
+               \caption{ \textbf{Results on Pittsburgh 25k dataset - bag-of-visual-words.}
+                     The fraction of correctly recognized queries (recall@K)
+                        in the top $K\in\{1,2,5,10,20\}$ retrieved images.
+                        % Different methods have been applied to two types of descriptors, the BOW and Fisher vectors compressed to different dimensions.
+The learnt representations (BOW \emph{e-SVM} and BOW \emph{p-val}) outperform the raw BOW baseline as well as the learnt representation without calibration (BOW raw SVM).
+                     The learnt descriptors by the proposed method (BOW e-SVM) marginally improve over the raw bag-of-visual-words descriptors (BOW).
+                     %on both the 25k and 55k Pittsburgh image datasets.     
+               }
+               \label{tab:recallBOW}
+               \end{centering}
+            \end{table}
             %
-         %
-         %
-         %
-         \begin{figure*}[h]
+            \begin{table}[b]
+               \begin{centering}
+                  \include{table55k}
+                  \caption{ \textbf{Results on Pittsburgh 55k dataset - Fisher vectors.}
+                     The fraction of correctly recognized queries (recall@K)
+                     in top $K\in\{1,2,5,10,20\}$ retrieved images.
+                     The proposed method (\emph{e-SVM}) has been applied to Fisher vectors compressed to different dimensions.
+                     The learnt descriptors by the proposed method (FV e-SVM) consistently improve over the raw Fisher vector descriptors across the whole range of $K$  and all dimensions.
+                  %on both the 25k and 55k Pittsburgh image datasets.     
+                  }
+               \label{tab:recall2}
+               \end{centering}
+            \end{table}
+
+   \begin{figure*}[h!t]
       \include{myFigureWnorm}
@@
           Note that the baseline methods often finds images depicting the same buildings but in a distance whereas our learnt representation often finds a closer view better matching the content of the query.
+{\bf Kindly find additional results in the supplementary material.}
       }
@@
    \end{figure*}
-         %
-         %
-         %
 
@@
       We have shown that a discriminative yet compact image representation for place recognition can be learnt using the exemplar support vector machine applied to Fisher vector image descriptors without the need for expensive and tedious calibration typical for other exemplar  support vector machine methods.
-      \textcolor{petr}{We demonstrate that proposed method is applicable to two different descriptors, the bag-of-visual-words and Fisher vectors.}
+We demonstrate that proposed method is applicable to two different descriptors, the bag-of-visual-words and Fisher vectors.
       Our results show significant gains in place recognition performance compared to raw Fisher vector matching as well as other baselines.
 Our work opens-up the possibility of learning a compact and discriminative representation using other descriptors such as HOG~\cite{Dalal05} or the recently developed convolutional neural network features~\cite{Donahue13,Krizhevsky12,Oquab14,Sermanet13} as well as extending the analysis to other cost functions~\cite{Gharbi12,Hariharan12}.
-
+\clearpage 
 \small{

### 2014-11-20 supplementary/supp.tex
Supplementary material

\documentclass[10pt,onecolumn,A4]{article}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% usepackages by Petr
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{hyphenat}
\setlength\textwidth{175mm}
\setlength\textheight{280mm}
\setlength\oddsidemargin{0mm}
\setlength\evensidemargin{0mm}
\setlength\topmargin{-25mm}
\setlength\headsep{0mm}
\setlength\headheight{0mm}
\setlength\leftmargin{0mm}

\definecolor{myGrey}{HTML}{33FF00}
\definecolor{myRed}{HTML}{FF3030}
\definecolor{myGreen}{HTML}{00FF00}
\definecolor{myGrey}{HTML}{AAAAAA}
\definecolor{myWhite}{HTML}{FFFFFF}
\definecolor{myCopper1}{HTML}{FFC77F}
\definecolor{myCopper2}{HTML}{FFAB6D}
\definecolor{myCopper3}{HTML}{E9915D}
\definecolor{myCopper4}{HTML}{BB754B}
\definecolor{myCopper5}{HTML}{935C3A}

\title{Supplementary material, paperID:954}
\begin{document}
	\maketitle

\begin{figure}
	\center
	\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=0.5\linewidth]{mapGoogle.png}
	\caption{ \textbf{A map corresponding to the area covered by database.}
		The Pittsburgh 25k dataset covers roughly an area of $1.3 \times 1.2 \; {\rm km}^2$.
	}
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1383/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1383/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/svm01.jpg}}
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/svm03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1383/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%\caption{Example sup1383} 
	\caption{ \textbf{Response of Fisher vector accross the databse images.}
		\emph{Top row:} The heatmaps show a distribution of the Fisher vector (FV) similarity score with a given query image. A location of the query image is shown by green circle, top 5 strongest peaks are denoted by a cross marker along with its rank. \emph{Bottom row:} The query image is shown in a gray box and top five database images corresponding to the top 5 strongest peaks in the map. The correct match is denoted by green bounding box.
		Each FV score votes into a max-pooling accumulation array that corresponds to a GPS location of the database images.
		\emph{Left} column shows results for raw FV baseline without any learning while \emph{right} column displays results for FV obtained by proposed method (e-SVM FV). Notice that e-SVM FV descriptor suppress the peaks that are far from the query image which results into a change of ranking.
		}
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1666/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1666/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/svm01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/svm03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1666/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%\caption{Example sup1666} 
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1693/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1693/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/svm01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/svm03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1693/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%%\caption{Example sup1693} 
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1812/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1812/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/svm01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/svm03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1812/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%%\caption{Example sup1812} 
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1957/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1957/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/svm01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/svm03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1957/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%%\caption{Example sup1957} 
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1962/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1962/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/svm01.jpg}}
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/svm03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup1962/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%%\caption{Example sup1962} 
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2358/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2358/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/svm01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/svm03.jpg}}
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2358/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%%\caption{Example sup2358} 
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2569/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2569/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/svm01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/svm03.jpg}}
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2569/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%%\caption{Example sup2569} 
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2602/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2602/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/svm01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/svm03.jpg}}
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2602/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%%\caption{Example sup2602} 
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2959/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2959/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/svm01.jpg}}
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/svm03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2959/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%%\caption{Example sup2959} 
\end{figure}

\begin{figure}
	\begin{minipage}{0.45\linewidth}
		\center
		(raw FV128 baseline) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2961/heatRaw.jpg}
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\center
		(e-SVM FV128) \\
		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup2961/heatSvm.jpg}
	\end{minipage} 
	\\
	\textcolor{myWhite}{xxx}\\
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/raw01.jpg}}
		\colorbox{myCopper2}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/raw02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/raw03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/raw04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/raw05.jpg}} \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage} 
	\begin{minipage}{0.45\linewidth}
		\colorbox{myGrey}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/query.jpg}}
		\colorbox{myCopper1}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/svm01.jpg}}
		\colorbox{myGreen}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/svm02.jpg}}	\\
		\textcolor{myWhite}{xxxxxx}Query \hspace{0.25\linewidth}1. \hspace{0.25\linewidth}2. \\
		\colorbox{myCopper3}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/svm03.jpg}}
		\colorbox{myCopper4}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/svm04.jpg}}
		\colorbox{myCopper5}{\includegraphics[trim = 55mm 40mm 55mm 30mm, clip=true,width=0.30\linewidth]{sup2961/svm05.jpg}}  \\
		\textcolor{myWhite}{xxxxxx}3. \hspace{0.25\linewidth}4. \hspace{0.25\linewidth}5. \\
	\end{minipage}
	%%\caption{Example sup2961} 
\end{figure}

\end{document}

### 2014-11-20 supplementary/supp.tex
updated text

@@
 
-\title{Supplementary material, paperID:954}
+\title{Supplementary material for submission \# 954\\
+Fisher vector places: learning compact descriptors for place recognition
+ }
 \begin{document}
@@
 	\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=0.5\linewidth]{mapGoogle.png}
-	\caption{ \textbf{A map corresponding to the area covered by database.}
+	\caption{ \textbf{A map corresponding to the area covered by image database.}
 		The Pittsburgh 25k dataset covers roughly an area of $1.3 \times 1.2 \; {\rm km}^2$.
@@
 		\center
-		(raw FV128 baseline) \\
+		FV128 (baseline, no learning) \\
 		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1383/heatRaw.jpg}
@@
 		\center
-		(e-SVM FV128) \\
+		FV128 e-SVM (proposed learnt compact descriptor) \\
 		\includegraphics[trim = 55mm 40mm 55mm 25mm, clip=true,width=\linewidth]{sup1383/heatSvm.jpg}
@@
 	%\caption{Example sup1383} 
-	\caption{ \textbf{Response of Fisher vector accross the databse images.}
-		\emph{Top row:} The heatmaps show a distribution of the Fisher vector (FV) similarity score with a given query image.
+%	\caption{ \textbf{Response of Fisher vector accross the databse images.}
+%		\emph{Top row:} The heatmaps show a distribution of the Fisher vector (FV) similarity score with a given query image.
 A location of the query image is shown by green circle, top 5 strongest peaks are denoted by a cross marker along with its rank.
@@
 The correct match is denoted by green bounding box.
-		Each FV score votes into a max-pooling accumulation array that corresponds to a GPS location of the database images.
-		\emph{Left} column shows results for raw FV baseline without any learning while \emph{right} column displays results for FV obtained by proposed method (e-SVM FV).
+%		Each FV score votes into a max-pooling accumulation array that corresponds to a GPS location of the database images.
+%		\emph{Left} column shows results for raw FV baseline without any learning while \emph{right} column displays results for FV obtained by proposed method (e-SVM FV).
 Notice that e-SVM FV descriptor suppress the peaks that are far from the query image which results into a change of ranking.
+%		}
+	\caption{{\bf Top:} 
+	Matching scores for the same query image shown across the entire database on the map.
+Brighter pixels indicate higher (better) scores.
+The ground truth position of the query image is shown as a green circle.
+The map also shows the position and rank of the top five matches.
+{\bf Bottom:} The top five matches for the same query before (left) and after (right) learning.
+	Note that the proposed method (right) correctly localized the query image within the top five matched locations. 
+	The matched image is shown in green. 
+	{\bf Animation:} The animation shows the score map for the same query with the raw FV descriptors and the proposed learnt compact descriptor.
+Note that the learnt descriptors better discriminate different places on the map and hence some of the high scoring false positive peaks for this query are suppressed.
+%	Note that the proposed method suppresses the high-scores far from the query image, which results in a change of ranking.}
 }
+%	
+%	\textbf{Response of Fisher vector accross the databse images.}
+%		\emph{Top row:} The heatmaps show a distribution of the Fisher vector (FV) similarity score with a given query image.
+A location of the query image is shown by green circle, top 5 strongest peaks are denoted by a cross marker along with its rank.
+\emph{Bottom row:} The query image is shown in a gray box and top five database images corresponding to the top 5 strongest peaks in the map.
+The correct match is denoted by green bounding box.
+%		Each FV score votes into a max-pooling accumulation array that corresponds to a GPS location of the database images.
+%		\emph{Left} column shows results for raw FV baseline without any learning while \emph{right} column displays results for FV obtained by proposed method (e-SVM FV).
+Notice that e-SVM FV descriptor suppress the peaks that are far from the query image which results into a change of ranking.
+%}
 \end{figure}
